# Introduction

## Stock Structure and Life History

Pacific Cod (*Gadus macrocephalus*) is a relatively short-lived, fast-growing member of the family Gadidae. Other common names in British Columbia (BC) include grey cod (or gray cod). Populations of Pacific Cod are distributed from California, throughout the waters of BC, Gulf of Alaska and the Bering Sea to Russia, Korea, Japan and China [@hart1973]. Maximum observed age in British Columbia is around 10-11 years [@westrheim1996, this document], while a maximum age of approximately 13 years has been reported for Alaskan stocks [@roberson2001]. Maximum length recorded in British Columbia is 100 cm [@hart1973], although some larger specimens have been observed in Alaska and Russia [@westrheim1996]. Pacific Cod are demersal spawners, with several studies reporting that spawning most likely occurs during February to March. A comprehensive review of the biology, life history and distribution of Pacific Cod in British Columbia is provided by @westrheim1996.

Four stocks of Pacific Cod are defined for management purposes on the BC coast: Strait of Georgia (4B); West Coast Vancouver Island (3CD); Queen Charlotte Sound (5AB); and Hecate Strait (5CD). This study focuses on the populations in Queen Charlotte Sound combined with Hecate Strait (5ABCD) and the West Coast Vancouver Island (3CD) (Figure XX).

Recent genetic analyses have identified a distinction between North American and Asian Pacific Cod populations, and have shown some evidence for distinction between Alaskan populations and those south of Dixon Entrance in British Columbia (reviewed in Appendix XX). There is also evidence that fish taken off the coast of Washington and the west coast of Vancouver Island may be distinct from fish sampled within the Strait of Georgia or Puget Sound. However, linkages, if any, among stocks in BC and those in Alaska remain poorly understood. To date it is uncertain whether genetic population structure exists within BC waters (Appendix XX).

Population dynamics of Pacific Cod in BC have been characterized by large variations in abundance, based on reconstructions driven by fishery catch rates, most likely as a function of large recruitment events followed by large opportunistic fishery catches. However, other hypotheses, including predator-prey cycles, density-dependent growth and mortality,and northward water transport have also been proposed (reviewed by @westrheim1996). Natural mortality has been estimated as high as 0.6 - 0.65 y-1 in some stock assessments (e.g., @fournier1983; @sinclair2005) although lower estimates (~0.4 y-1) have also been obtained [@sinclair2001]. The combination of apparently volatile dynamics with short life span and high natural mortality suggests periods of over/under harvest could result if harvest strategies are not designed to be robust to these features. However, in the context of the BC integrated groundfish fishery, constraints imposed by quotas for other species mean that single-species considerations alone do not always dictate the best harvest strategy.

## Ecosystem Considerations

### Prey and Predators

Pacific Cod are omnivores, eating a diet of mainly marine invertebrates, including amphipods, euphausiids, shrimp and crabs. At around 50-55 cm they also become piscivorous, with Pacific Sand Lance (*Ammodytes hexapterus*) and Pacific Herring (*Clupea harengus pallasi*) becoming important components of the diet [@westrheim1996]. Juvenile Sablefish (*Anoplopoma fimbria*) and adult Pacific Hake (*Merluccius productus*) have also been reported in the diet of Pacific Cod off the west coast of Vancouver Island @ware1986. Pacific Cod have been reported in the diets of Pacific Halibut (*Hippoglossus stenolepis*), North Pacific Spiny Dogfish (*Squalus suckleyi*), sea birds, seals and sealions @westrheim1996.

@walters1986 demonstrated a Pacific Cod-Herring predator-prey interaction in Hecate Strait, in contrast to @ware1986. Simulation models were developed by @walters1986 to explicitly model the effects of Pacific Cod predation on Pacific Herring. The simulations were able to mimic recruitment trends in both species. @walters1986 concluded that availability of Pacific Herring prey could be an important driver of Pacific Cod production in Hecate Strait, and, similarly, that Pacific Cod predation could be a significant driver of Pacific Herring abundance. These authors acknowledged that there are alternative hypotheses for cycles in abundance of Pacific Cod and Pacific Herring (e.g., environmental forcing; see below) and suggested that large-scale management experiments may be the only way to distinguish among competing hypotheses.

### Environment

A large number of studies have investigated linkages between recruitment and environmental indices for Pacific Cod in Hecate Strait. The dominant hypothesis is an inverse relationship between recruitment and northward water transport (i.e., northward advection of larvae) (@tyler1986; @tyler1991). Northward water transport has been shown to be positively correlated with mean annual sea level at Prince Rupert during the spawning season, which in turn has been used as an explanatory variable for recruitment by a number of authors [@fournier1983]; [@sinclair2001]; @sinclair2005-2; @sinclair2005). @westrheim1996 provides a review of the major alternative studies.

### Other species

Other species caught with Pacific Cod include Arrowtooth Flounder (*Atheresthes stomias*), Yellowtail Rockfish (*Sebastes flavidus*), Pacific Ocean Perch (*S. alutus*), Lingcod (*Ophiodon elongatus*), Silvergray Rockfish (*S. brevispinis*), English Sole (*Parophrys vetulus*) and Big Skate (*Raja binoculata*) (Figure XX). Vessels catching Pacific Cod must hold quota for all quota species encountered. Since 1996, there has been 100% at-sea observer coverage on commercial bottom trawl vessels in BC. At-sea releases are recorded by observers and counted against the vessel's quota, according to agreed-upon discard mortality rates published in the integrated fishery management plan [@dfo2015]).

## Fisheries

Pacific Cod in British Columbia are caught almost entirely in the groundfish bottom trawl fishery, which is part of BC's integrated groundfish fishery. Pacific Cod is one of the principal target species of the trawl fishery in Hecate Strait. Currently, the majority of the BC Pacific Cod catch is taken from in Hecate Strait (Area 5CD) (Figure XX).

Pacific Cod are distributed throughout Area 5CD at depths mainly less than 150 m. Pacific Cod density, measured by commercial catch per unit effort (see Appendix XX), appears to be highest over the Two Peaks/Butterworth, White Rocks, Shell Ground, Reef Island, and Horseshoe fishing grounds (Figure XX). In Queen Charlotte Sound (Area 5AB), Pacific Cod are caught mainly around the edge of Goose Island Bank in Area 5B and on Cape Scott and Mexicana Banks, north of Vancouver Island, in Area 5A (Figure XX). The depth range of capture is approximately 60--160 m. Annual reported catches of Pacific Cod in both Hecate Strait and Queen Charlotte Sound have shown considerable variability since the beginning of the time series in 1956 (Figure XX, Tables XX and XX).

In Hecate Strait (Figure XX), major peaks in catches (landings plus estimated discards) occurred in 1958 (5,702 t), 1965 and 1966 (8,870 t and 9,156 t), 1979 (5,736 t), 1987 (9,542 t), and 1991 (7,747 t). These peak years may be contrasted with years of low catches in 1961 (1,528 t), 1970 and 1971 (1,188 t and 1,333 t), 1985 (1,053 t), and the minimum on record in 2001 (214 t). Reported catches have increased since 2001 to 701 t in 2012, although it should be noted that recent low catches are partially a result of lowered quotas in the early to mid-2000s. Catch was reported by USA vessels from 1956 to 1978. The estimated USA portion of the total catch was approximately 15% over these years (Table XX).

Catches in Queen Charlotte Sound (Figure 3b) also showed significant variability over the time series. Major peaks in catches occurred in1957 (2,625 t), 1965 (1,983 t), 1972 and 1975 (2,415 t and 2,470 t), 1987 (3,209 t), and 1991 (2,206 t). Low catch years included 1961 (259 t), 1970 (278 t), 1983 (184 t), 2000 (67 t) and the lowest year on record 2008 (35 t). Significant catches were reported by USA vessels from 1956 to 1980. The estimated USA portion of the total catch was approximately 50% over these years (Table XX).

Prior to the introduction of at-sea observer coverage in 1996, estimates of at-sea releases (discards) for the period 1956-1995 were obtained from fishing logbooks (Figure XX). These estimates are considered an underestimate of the actual releases. Estimates in years following the introduction of 100% at-sea observer coverage in 1996 can be considered to be more accurate. Since 1996, the proportions of estimated discards have been considerably higher than in years before at-sea observers (Figure XX), especially in Queen Charlotte Sound, largely as a result of reduced total catches. Pacific Cod can be legally discarded by trawlers in BC. However, on-board observers first estimate the quantity being discarded and it is assigned a discard mortality rate which is counted against the vessel's Pacific Cod quota. Therefore, in addition to greater accuracy in reporting of discards since 1996, incentives to avoid discarding have also been greater.

Japanese and Soviet vessels also trawled in waters off BC in the late 1960s and early 1970s. These vessels were mainly targeting rockfish and likely at depths greater than 150 m. The bycatch of Pacific Cod in these fisheries is, however, unknown. Given uncertainty in foreign catches and discards in the earlier parts of the time series, total catch estimates should be considered underestimates prior to 1996.

Bottom trawl fishing effort has been somewhat cyclic in both areas, especially in Hecate Strait (Figure XX). Total effort of all trawl vessels has declined in both areas since peaking in 1993 (Hecate Strait) and 1995 (Queen Charlotte Sound). A detailed analysis of catch per unit effort (CPUE) is provided in Appendix B. As noted by Sinclair (2000), however, there are a number of problems with the use of commercial catch per unit effort data as an index of biomass for Pacific Cod. It has been suggested that changes in the management regime from an unrestricted fishery prior to 1992, to the introduction of TACs (1992-1996) and then to Individual Vessel Quotas (IVQs) (1997-present), as well as several increases in mesh size, have affected the underlying relationship between commercial CPUE and abundance, and the relationship between fishing effort and fishing mortality. In recent years of lower Pacific Cod quotas, many fishing masters report actively avoiding Pacific Cod to prevent their Pacific Cod quota being exceeded before catching available quotas for other species. @fournier1983 noted similar problems with relating fishing effort to fishing mortality for this fishery. @sinclair2001 analyzed the spatial distribution of fishing effort in Hecate Strait and reported that there had been little fishing over Butterworth, White Rock, Bonilla and Horseshoe grounds (Figure XX), which had previously been locations with the highest CPUE. They also cited industry reports that key Pacific Cod fishing grounds had been avoided to preserve Pacific Cod quota for bycatch in other fisheries [@sinclair2001]. We do not provide a detailed analysis of spatial fishing effort in this document but recommend it as an avenue of future research to improve understanding of the CPUE data and drivers of fishing effort (e.g., @branch2008).

## Management History

The history of Pacific Cod management from 1984 to 2013 is summarized in Tables XX--XX. The tables list total allowable catches (TACs), landings and carryovers, area closures and mesh restrictions.

Groundfish fisheries were managed by calendar year until 1996. Beginning in 1997-98 the fishing year changed to April 1--March 31. In 2010--2011 the fishing year was changed again to February 21 to February 20. Throughout this document, fishing years are defined as beginning April 1 for all years, and are referenced by starting year, e.g., fishing year 1997 runs from April 1, 1997 to March 31, 1998.

### Area 5AB: Queen Charlotte Sound

Annual TACs were introduced for Pacific Cod in Queen Charlotte Sound in fishing year 1997 (Table XX). Before 2005, there was no scientific advice for this area and the TAC was initially established at 260 t, which was the low end of the range of observed catches [@sinclair2005]. The TAC remained unchanged until 2004 when it was increased to 390 t based on advice from the fishing industry to Fisheries Management that Pacific Cod abundance had increased. There were also carryover amounts in the 1999-2004 fishing years. Between 1997 and 2002, the fishery did not catch the TAC (plus carryover) in each year, with a low of 18% taken in 2000 and a high of 56% in 2002. The TAC plus carryover was exceeded by 16% in 2003. The TAC remained at 390 t from 2004 until 2010. In 2010 the quota was exceeded by 22% and in 2011 the TAC was increased to 590 t.
Other management measures have been used to control the Pacific Cod fishery in Area 5AB. Voluntary increases in mesh size for various portions of Queen Charlotte Sound were suggested in 2007 for vessels fishing shallower than 60 fm. This was then regulated in 2011 (Table XX).

### Area 5CD: Hecate Strait

Annual TACs were introduced in the 5CDE area in 1992 [@sinclair2005]. Catches in Area 5E (West Coast Haida Gwaii) have been negligible and we do not further discuss this area. The original Area 5CD 1992 TAC was 3,400 t and landings that year exceeded this figure by 48% (Table XX). The TAC was increased to 5,100 t in 1993, and then reduced in steps to 1,000 t in 1998. The low catch in relation to the TAC in 1999 led to a carryover of 283 t in 2000. The TAC was reduced to 200 t in 2001 due to very low assessed stock biomass [@sinclair2000] and no carryovers were allowed. The TAC was maintained at 200 t in 2002. The 2003 TAC was initially set at 200 t but results from the Hecate Strait Pacific Cod monitoring survey, commercial CPUE, and input from the trawl fleet indicated that Pacific Cod abundance had increased in the area. Consequently, the TAC was increased to 400 t in the winter of 2003 and the TAC was maintained at 400 t for 2004. The TAC was increased to 800 t in 2005 and remained at that level until 2009. In 2010 the TAC was increased to 1,200 t and has remained at that level until the present.

Other management measures have been used to control the Pacific Cod fishery in Area 5CD. Voluntary increases in mesh size for various portions of areas 5CD were suggested as early as 1989 for this fishery and were regulated in 1995 (Table XX). There have also been a number of closures instituted in Hecate Strait to protect spawning biomass (Table XX, Figure XX). The Horseshoe and Reef Island fishing grounds, as well as the shallow Dogfish Bank, were closed from January 1--April 15 in 1991 and 1992. A slightly smaller area was closed for the same months between 1996 and 2001 (Table XX, Figure XX). The closed area was again increased in size in February 2001 to include all of Hecate Strait south of a line between the latitude of Rose Spit and north of a line just south of Reef Island (Figure XX). This closed all of the main cod fishing grounds except Two Peaks/Butterworth. Effective January 27, 2012 the size of the spawning closure was decreased, opening up the eastern side of Hecate Strait to fishing, including the White Rocks ground (Figure 6). Additionally, since 1996, there has been a closure from June 1-July 15 in the shallow portions of Area 5D for the protection of Dungeness crabs during the soft shell stage.

### Area 5CD: Hecate Strait

TO DO. Waiting for GMU to send historical TACs. RF to check 2001 and 2002 assessments.

## Assessment History

A number of methods have been used to assess Pacific Cod in Hecate Strait since the 1980s. @fournier1983 developed an age-structured model and used it to test for evidence of age-dependent trends in natural mortality, density-dependent natural mortality and catchability, and also for evidence of an environmental factor affecting recruitment. Evidence was found for a relationship between mean sea level at Prince Rupert and recruitment, and also for density-dependent natural mortality. Natural mortality was estimated to be 0.65 y-1 by @fournier1983. This author cautioned about the possibility of confounding among model parameters and systematic data biases that could influence conclusions from the analysis. Estimates of age were obtained from length-frequency analysis [@foucher1982].

Pacific Cod are one of the most difficult Pacific groundfish species to age. Annual rings (annuli) in otoliths, other bony structures and scales are difficult to distinguish from interannual growth checks (@beamish1981; @chilton1982; @roberson2001; @johnston2012). In British Columbia, age compositions have been estimated using length-based approaches, scales, otoliths and, currently, dorsal fin ray sections, although all methods present difficulties. In the absence of reliable direct age data, length-based approaches were used to assess the Hecate Strait stock during the 1990s [@haist1995; 1996; 1997; 1998]. The last of these assessments [@haist1998] suggested that the stock had reached an historic low in 1996, followed by a slight rebound.

@sinclair2000 used a simple surplus production model fit to a commercial CPUE index to assess the Hecate Strait stock in 2000. This author cited significant structural changes in the fishery during the 1990s resulting in changes in quality and comparability of fishery-dependent data available for the analysis. Changes included voluntary increases in mesh size in the commercial fishery and introduction of individual vessel quotas (IVQs) in 1997 as discussed above. Given the large structural differences between the previous length-based models and the surplus production model, @sinclair2000 noted that results were remarkably comparable until 1994, with three estimated peaks in abundance occurring in 1965, 1974-5 and 1986-7. The two approaches diverged significantly after 1994, with the the length-based Multifan model estimating an increase in biomass while the surplus production model estimated a decline. The differences were interpreted to be due to differences in the indices of abundance used to tune the models, as well as structural model differences.

@sinclair2001 developed a delay-difference model (@deriso1980; @schnute1985; @hilborn1992) containing a Ricker stock-recruit function to assess Pacific Cod in Hecate Strait and off the west coast of Vancouver Island. Recruitment was assumed to be knife-edged at age 2 years. A report card summary of information available for the stock was also developed. The report card analysis from this assessment found biomass indicators to be in the "danger" and "low" categories with potential for increasing recruitment; and reported a general lack of information on other types of indicators for this species in BC. The delay difference model provided a better statistical fit to the data than the previously-applied surplus production model. However, biomass estimates followed a similar trend and magnitude (Figure XX). Retrospective analyses using only data up to 1995 tended to project large increases in biomass that were not predicted when the most recent CPUE data to 2000 were used. The authors noted that the model containing the most recent data predicted the stock to be less productive than the model containing only the earlier data.

TO DO. Add notes about 3CD

The Hecate Strait Pacific Cod stock was last assessed in 2004 [@sinclair2005] using a delay difference model with a Beverton-Holt stock-recruit function, based on the view that a Ricker type function with declining recruitment at high stock size was inappropriate for this species. As for the previous assessment, recruitment was assumed to be knife-edged at age 2 years. Model fits were presented with alternative combinations of fixing or estimating natural mortality (M) and the steepness parameter of the stock-recruit function, [@mace1988]. They reported similar fits and biomass estimates for the alternative scenarios but noted very different estimates of equilibrium MSY-based management parameters under alternative combinations of fixed and estimated steepness and M.

Estimates of biomass for the two preferred model runs were considerably higher than estimates from previous assessments (Figure XX). Given structural differences between these and previous models, and differences in the data to which the models were fitted, it is not appropriate to speculate on the source of the large difference in scale among models. However we note that the 2004 assessment was not directly fit to the commercial CPUE data as were previous assessments, but instead was fit to data from the Hecate Strait Assemblage Survey [@choromanski2005] and the Pacific Cod Monitoring Survey [@sinclair2002. There were also differences in:

* weighting of the indices of abundance relative to the mean weight data, to which both sets of models were also fitted; and
* the choice of other fixed variance parameters.

Key uncertainties of the analysis noted by @sinclair2005 were:

* uncertainty in the growth function (model parameters and assumptions of stationarity); and
* the possibility of violating the assumption of knife-edged recruitment at age 2 years, given evidence for younger
  fish in the length composition data from the commercial fishery.

  TO DO. Edit above to include 3CD

# DATA SOURCES

## DATABASES
Data were extracted from a number of different databases:

**GFBio**
Biological samples and research cruise database. Groundfish Section, Marine
Ecosystems and Aquaculture Division, Science Branch, Fisheries and Oceans Canada,
Pacific Biological Station. This data archive includes most of the groundfish
specimen data collected since the 1950s. It therefore includes data from a variety
of sources (port and at-sea commercial sampling, research survey sampling),
collected using a variety of sampling methods.

**GFCatch**
Canadian trawl landings, 1954-1995 [@rutherford1999].

**PacHarvTrawl**
Canadian trawl landings, 1996 to March 31, 2007. SQL Server database, Groundfish
Section, Marine Ecosystems and Aquaculture Division, Science Branch, Fisheries
and Oceans Canada, Pacific Biological Station.

**GFFOS**
Canadian trawl landings, April 1, 2007 to 2018. View of the Fisheries and Oceans
Canada (DFO) Fishery Operations (FOS) database. Groundfish Section, Marine
Ecosystems and Aquaculture Division, Science Branch, Fisheries and Oceans
Canada, Pacific Biological Station.

## Catch Data
Commercial fishing data are presented in this document by fishing year which
includes the period April through March, e.g., fishing year 1956 comprises
the period April 1, 1956 to March 31, 1957. Landings data are presented
separately for Canada and the USA (Tables XX and XX). Combined USA-Canada
landings data were obtained from the Pacific Marine Fisheries Commission
reports for 1956-1981 and the USA landed portion was determined by subtracting
the Canadian landed amount from the combined total for each year. In cases where
the difference was negative, the USA landed amount was set to zero
(Tables XX and XX). Canadian data were obtained: from the GFCatch database for
the period 1954-1995 [@rutherford1999]; from the PacHarvest database for the
period 1996-March 31, 2007; and from the Fisheries and Oceans Canada (DFO) FOS
database for the period April 1, 2007 until the present. The annual size
composition of commercial catches and landings were estimated from port samples
and at-sea samples collected by observers archived in the GFBio database.

## Indices of abundance

### Hecate Strait Assemblage Survey

A series of multi-species groundfish bottom trawl surveys was conducted in
Hecate Strait in May-June of 1984, 1987, 1989, 1991, 1993, 1995, 1996, 1998,
2000, 2002, and 2003 @westrheim1984, @fargo1984, @fargo1988,
@wilson1991, @hand1994, @workman1996, @workman1997, @choromanski2002).
The results up to 2000 were reported in the 2001 assessment
[@sinclair2001] and results from 2002 and 2003 were presented in the
2005 assessment [@sinclair2005].

The original design of this survey assigned fishing locations by 10 fm depth
intervals within a 10 nm grid of Hecate Strait. The survey was
post-stratified for the purpose of calculating an abundance index for Pacific
Cod [@sinclair2000]. The post stratification used 10 fm depth intervals for
the entire survey area, thereby treating each depth interval as a single
stratum.

The Hecate Strait Assemblage survey was designed as a systematic
fixed-station survey. Despite attempts to apply post-sampling stratification,
this approach had high survey variance [@sinclair2007]. In 2004 the Hecate
Strait Assemblage survey was discontinued in favour of the Hecate Strait
Synoptic survey (described below).

### Hecate Strait Synoptic Survey

The Hecate Strait synoptic groundfish bottom trawl survey is part of a
coordinated set of long-term surveys that together cover the continental shelf
and upper slope of most of the BC coast. The Hecate Strait synoptic survey has
been conducted during May-June, in odd years since 2005. All the synoptic
surveys follow a random depth stratified design. The survey area is divided
into 2 km by 2 km blocks and each block is assigned to one of four depth
strata based on the average bottom depth in the block. The four depth strata
for the Hecate Strait survey are 10--70m, 70--130m, 130--220m, and
220--500m. Each year blocks are randomly selected within each depth strata.
The relative allocation of blocks amongst depth strata was determined by
modeling the expected catches of groundfish and determining the target number
of tows per stratum that would provide the most precise catch rate data for
as many species as possible.

### Queen Charlotte Sound Synoptic Survey

The Queen Charlotte Sound synoptic groundfish bottom trawl survey is part of
a coordinated set of long-term surveys that together cover the continental shelf
and upper slope of most of the BC coast. The Queen Charlotte Sound survey has
been conducted in July-August in 2003, 2004 and in odd years since 2005. All
the synoptic surveys follow a random depth stratified design. The survey area
is divided into 2 km by 2 km blocks and each block is assigned to one of four
depth strata based on the average bottom depth in the block. The four depth
strata for the QCS survey are 50--125m, 125--200m, 200--330m,
and 330--500 m. Each year blocks are randomly selected within each depth strata.
In addition, for the purposes of allocating blocks, the QCS survey is divided
into northern and southern spatial strata.

The relative allocation of blocks amongst depth strata was determined by
modeling the expected catches of groundfish and determining the target number
of tows per stratum that would provide the most precise catch rate data for as
many species as possible.

### West Coast Vancouver Island Synoptic Survey

TO DO

### Survey index of abundance: Canadian Synoptic Surveys, swept area analysis
TO DO possibly add this to Appendix called Fishery Independent Surveys including Paul's write up of the NMFS Triennial

For all surveys, a swept area estimate of biomass in any year y was obtained
by summing the product of the CPUE and the area surveyed across the surveyed
strata $i$:

\begin{equation}
  B_y = \sum_{i=1}^kC_{y_i}A_i=\sum_{i=1}^kB_{y_i}
  (\#eq:sweptareabiomass)
\end{equation}

where
$C_{y_i}$ = mean CPUE density (kg/km^2^) for Pacific Cod in stratum $i$
$A_i$ = area of stratum $i$ (km^2^), and
$B_{y_i}$ = biomass of Pacific Cod in stratum $i$ for year $y$
$k$ = number of strata

CPUE ($C_{y_i}$) for Pacific Cod in stratum $i$ for year $y$ was
calculated as a density in kg/km^2^ by

\begin{equation}
  C_{y_i}=\frac{1}{n_{y_i}} \sum\limits_{j=1}^{n_{y_i}} \frac{W_{y_i,j}}{D_{y_i,j}w_{y_i,j}}
  (\#eq:sweptareacpue)
\end{equation}

where
$W_{y_i,j}$ = catch weight (kg) for Pacific Cod in stratum $i$ for year $y$ and tow $j$
$D_{y_i,j}$ = distance travelled (km) by tow $j$ in stratum $i$ for year $y$
$w_{y_i,j}$ = net opening (km) by tow $j$ in stratum $i$ for year $y$
$n_{y_i}$ = number of tows in stratum $i$

The variance of the survey biomass estimate $V_y$ for Pacific Cod in year $y$
is calculated in kg^2^ as follows:

\begin{equation}
  V_y=\sum_{i=1}^k\frac{\sigma_{y_i}^2A_i^2}{n_{y_i}}=\sum_{i=1}^kV_{y_i}
  (\#eq:sweptareavariance)
\end{equation}

where $\sigma_{y_i}^2$ is the variance of the CPUE in $kg^2/km^4$ for year $y$ in
stratum $i$, $V_{y_i}$ is the variance of Pacific Cod in stratum $i$ for year $y$,
where $\sigma_{y_i}^2$ was obtained from bootstrapped samples (see below).

The CV for Pacific Code for each year $y$ was calculated as follows:

\begin{equation}
  (CV)_y=\frac{{V_y}^{1/2}}{B_y}
  (\#eq:sweptareacv)
\end{equation}

where $(CV)_y$ is the CV for year $y$.

One thousand bootstrap replicates with replacement were constructed from the
survey data to estimate bias corrected 95% confidence regions for each survey
year [@efron1982].

### NMFS Triennial Survey (in Canadian waters)

## Biological data

*TO DO. Add dynamic references to Appendix A for annual mean weight, age and length data*

The methodology for calculating the mean weight of Pacific Cod from commercial
vessels for the years 1956--2017 is presented in Appendix A.

# Stock Assessment Model

All models presented in this document are Bayesian models implemented in
AD Model Builder [@fournier2012]. The models are based on the Integrated
Statistical Catch Age Model (iSCAM), developed by Steven J.D. Martell
[@martell2011]. A number of modifications have been made to the code by the
first author of this assessment to include delay difference calculations and
adapt the code for the purpose of assessing Pacific Cod in BC, as described
below. The model in its present formulation is fully described in the present
document.

# Reference Points and Harvest Control Rule

The DFO Fishery Decision-making Framework Incorporating the Precautionary
Approach (PA) policy [@dfo2009] requires stock status to be characterized using
three reference points:

- a Reference Removal Rate
- an Upper Stock Reference point (USR)
- a Limit Reference Point (LRP)

Provisional values of $USR = 0.8B_{MSY}$ and $LRP = 0.4B_{MSY}$ are
suggested in the absence of stock-specific reference points. The framework
specifies a limit reference removal rate of $F_{MSY}$. Therefore, we refer to
the reference removal rate as the limit removal rate (LRR) throughout this
document.

A harvest control rule based on these reference points that is coincident
with the choice of LRP, USR and LRR would apply a linear reduction in fishing
mortality as the stock falls below the USR, and would cease fishing when the
stock reaches the LRP (but see @cox2013). This is illustrated for a
hypothetical stock in Figure XX, where the USR and LRP are shown as vertical
lines and the removal rate is shown as a blue line. We make the observation
that the rate at which the fishing mortality should be reduced is unspecified
in the PA policy, but is usually depicted as a linear ramp between the USR
and LRP (Figure XX).

As already noted, large uncertainties in the productivity parameters natural
mortality (M) and steepness of the stock-recruit relationship (h) have resulted
in substantial uncertainties in MSY-based reference points for Hecate Strait
Pacific Cod in previous assessments [@sinclair2005]. Given uncertainty in
productivity parameters for this stock, @sinclair2005 suggested using
alternative reference points based on the reconstructed history of the stock.
They recommended the Limit Reference Point to be the minimum spawning biomass
from which the stock recovered to above average levels. This was estimated
to have occurred in 1971 (i.e., $LRP = B_{1971}$). @sinclair2005 suggested
long-term average Biomass ($B_{Avg}$) as a candidate proxy Upper Stock
Reference and long-term average harvest rate ($U_{Avg}$) as a proxy for the
reference removal rate.

@sinclair2005 acknowledged that the absolute estimate of biomass in 1971
is dependent on model formulation (e.g., see Figure XX), but found that most
model formulations agreed that 1971 was the year in which the stock was lowest
and subsequently recovered to above average levels. Therefore, they
recommended the LRP be set at $B_{1971}$ estimated by the assessment model,
rather than the absolute 1971 biomass estimated in their specific stock
assessment. The Groundfish Subcommittee of PSARC [@fargo2005] subsequently
recommended the use of $B_{1971}$ as the LRP for the Hecate Strait stock.
While there is no precedent for reference points in Queen Charlotte Sound,
the minimum stock size from which the biomass was estimated to have
recovered in this assessment occurred in 1985. $B_{1985}$ was therefore
proposed as the LRP for Queen Charlotte Sound.

Based on the recommendations of the 2005 Scientific Review Committee
[@fargo2005], we recommend continued use of historical-based reference points
for the present assessment cycle. However, we note that the recommendation
of @fargo2005 was unclear as to whether the calculation of average biomass
and fishing mortality should continue to be fixed for the period 1956-2004,
or whether the average should be updated to include recent years. In a later
section, we show that there is little difference between the estimated
average biomass for the period 1956-2004 compared to the period 1956-2017.
For consistency and stability, we suggest continuing to use averages based
on the shorter period 1956-2004.

A list of candidate reference points to use in decision tables for Pacific Cod
is shown in Table XX. In addition to the LRR, LRP and USR discussed above,
two benchmark measures are also included:

- $F_{2013}$
- $B_{2014}$

These will be used in the decision tables to show whether:

- fishing mortality is projected to increase or decrease under alternative
  2018 projected catch levels; and
- whether biomass is projected to increase or decrease under alternative
  2018 projected catch levels. Estimates of other candidate reference points,
  based on MSY calculations; and historical averages based on a longer time
  period are presented for comparison but are not used in decision tables.

The list of performance measures that will be used in decision tables for the
Pacific Cod stocks in Hecate Strait and Queen Charlotte Sound (Area 5ABCD) is
given in Table XX. Biomass-based performance measures were calculated as
projected 2019 biomass relative to reference points, under alternative 2018
projected catch levels. Fishing mortality-based performance measures were
calculated as projected 2018 fishing mortality relative to the reference points,
under alternative 2018 projected catch levels. We did not explore any
alternative reference points in this assessment (e.g., reference points based
on spawning biomass per recruit; @clark1991), but recommend exploration and
simulation-testing of alternatives in the context of a feedback simulation
analysis.

# Bridging Analysis

In Appendix XX we present a bridging analysis, beginning with a model that
emulated the results of the 2013 stock assessment with fixed parameters,
through steps that: updated the data streams to 2017; examined the effects
of model reconfiguration; and illustrated the effects of fixing variance terms.
A bridging analysis provides a means of documenting the transition from the
approach used by @forrest2013, and aids in understanding the underlying causes
of changes to the stock reconstruction and estimates of key parameters.
For brevity, we do not present the full suite of sensitivity analyses that were
explored but list key steps leading up to development of the candidate Base
Case models.

# Base Case Models

The Base Case models for both areas 5ABCD and 3CD are XX.

## Prior Probability Distributions

Prior probability distributions for the Area 5ABCD and 3CD Base Case models
are shown in Figure XX and Table XX.

Broad, uniform prior probability distributions were used for $ln(R_0)$,
$ln(R_{Avg})$, $ln(R_{Avg\_init}$) and $ln(q_{CPUE}$), where the subscript
CPUE indicates the commercial CPUE data from 1956-1995. These uniform
distributions reflect our ignorance the scale of the population.

A Beta distribution was used for steepness with shape parameters that
resulted in a distribution with mean = 0.7 XX and SD = 0.15 XX. These parameter
choices resulted in a distribution with almost no probability density for
values less than 0.2 XX, implying that no transformation was necessary
(Figure XX). @sinclair2005 fixed steepness at 0.75 in one of their
"preferred" scenarios. In their other "preferred" scenario, the MPD estimate
of steepness was 0.53. The prior probability distribution chosen here
encompasses both of these values. A sensitivity analysis was done for
both areas with a uniform distribution for steepness between 0.21 XX and
0.99 XX, with very little impact on posterior estimates of biomass
(see below).

A normal distribution was used for $ln(M)$ with mean = $ln(0.5)$  XX
and SD = 0.1 XX. @sinclair2005 obtained MPD estimates of natural mortality
of 0.596 and 0.567 in their two "preferred" scenarios. The bridging
analysis provided in Appendix XX of this document suggested that natural
mortality could be considerably lower, depending on the values of other
fixed or estimated parameters. For the base cases presented here, we chose
to centre the prior probability distribution a little lower than the MPD
values reported by @sinclair2005. Model sensitivity to both the mean and
the standard deviation of the distribution is presented below.

Normal distributions were used for $ln(q_{HSAS})$, $ln(q_{HSSS})$, and
$ln(q_{QSSS}$ where the subscripts $HSAS$, $HSSS$, and $QSSS$ indicate
the Hecate Strait Assemblage Survey, Hecate Strait Synoptic Survey, and
the Queen Charlotte Sound Synoptic Survey respectively (Table XX). Normal
distributions centred on $ln(1.0)$ were selected because the survey estimates
of biomass were derived from swept area analysis
(Eqs. \@ref(eq:sweptareabiomass)--\@ref(eq:sweptareacpue)) and could therefore
reasonably be expected to be some fraction of unity. A large standard
deviation was used to reflect ignorance of the scale of the swept area
analysis compared with the true biomass. Note there was no Assemblage Survey
in Queen Charlotte Sound (Area 5AB). Broad uniform distributions were used
for $ln(q_{CPUE})$, reflecting large uncertainty in the scale of the
relationship between commercial CPUE data and true biomass.

A total of XX model parameters were conditionally estimated in Area 5ABCD;
while XX parameters were estimated for Area 3CD, which had one fewer survey
q parameters (Table XX).

# Results

## Area 5ABCD: Queen Charlotte Sound and Hecate Strait

The joint posterior distribution was numerically approximated using the
Markov Chain Monte Carlo routines built into AD Model Builder
[@fournier2012]. Posterior samples were drawn systematically every 50,000 XX
iterations from a chain of length 100 million XX, resulting in 2,000 XX
posterior samples (the first 1,000 XX samples were dropped to allow for
sufficient burn-in). Convergence was diagnosed using visual inspection of the
trace plots (Figure XX) and visual examination of autocorrelation in posterior
chains (Figure XX). Autocorrelation was minor for most parameters, except for
$ln(R_{Avg\_init}$), for which autocorrelation was quite strong. This likely
reflects lack of information in the data about this parameter. Overall, there
was no strong evidence for lack of convergence, although the model occasionally
estimated very large values for $ln(R_0)$, possibly because of this parameter
was confounded with steepness ($h$, Figure XX). Very high estimates of
$ln(R_0)$ were obtained when $h$ was estimated to be very low (Figure XX).
Survey catchability parameters were positively correlated with each other
and negatively correlated with $ln(M)$, implying that there is limited
information in the data to distinguish between a small productive population
or a larger, less productive population (Figure XX).

Maximum posterior density (MPD) model fits to the three indices of abundance
are shown in Figure XX. Model-estimated indices of abundance followed the
general trends of all three observed trends, although they failed to reach most
of the peaks in the respective datasets. As previously discussed above and in
the bridging analysis (Appendix XX), model outcomes, especially estimates of
productivity parameters, were very sensitive to the goodness of fit to the
indices of abundance, particularly peak commercial CPUE observations and the
2017 Synoptic Survey observation (Table XX). We consider the goodness of fit
to the indices of abundance to be a primary driver of uncertainty in this
assessment and present further sensitivity analyses in a later section.

Posterior probability distributions of estimated parameters are shown in
Figure XX. The median, 2.5^th^ percentile and 97.5^th^ percentile posterior
parameter estimates, and maximum posterior density (MPD) estimates, are given
in Table XX. With the exception of steepness, the posterior estimates did not
appear to be strongly influenced by the prior probability distributions. The
posterior probability distribution for steepness was very similar to the prior
probability distribution, implying that there is little information about this
parameter in the available data. Sensitivity to the prior distribution assumed
for steepness is tested in a later section. Posterior probability estimates of
$ln(M)$ tended to be lower than the prior values, although the right-hand tail
of the posterior distribution did overlap with the left-hand tail of the prior
distribution (Figure XX). We have already noted that posterior estimates of $M$
were strongly influenced by the fit to the index of abundance data (Table XX),
which likely has a stronger influence on estimates of $M$ than the prior
probability distribution.

Normal prior probability distributions were used for the log catchability
parameters $ln(q)$ for the Hecate Strait Assemblage and Synoptic Surveys
(Figure XX). These prior probability distributions did not appear to strongly
affect the posterior estimates, with the posterior distribution far to the left
of the prior distribution in both cases (Figure XX).

Spawning biomass is shown in Figure \@ref(fig:fig-base-biomass).

### Reference Points

Posterior estimates of $F_{2017}$ and $B_{2018}$ are shown in Figures XX and
XX, and Table XX. Fishing mortality in 2017 was low compared to the historical
period, with the posterior median estimated to be 0.052y^-1^ XX.

## AREA 3CD: WEST COAST VANCOUVER ISLAND

Posterior samples were drawn systematically every 50,000 XX
iterations from a chain of length 100 million XX, resulting in 2,000 XX
posterior samples (the first 1,000 XX samples were dropped to allow for
sufficient burn-in). Convergence was diagnosed using visual inspection of the
trace plots (Figure XX) and visual examination of autocorrelation in posterior
chains (Figure XX).

### Reference Points

Alternative reference points based on estimates of average historical biomass,
similar to those adopted in Area 5ABCD, were explored.

# Sensitivity Analyses

We present a number of sensitivity analyses to show the influence of certain data sources, fixed
parameters and prior probability distributions in the Area 5ABCD and 3CD Base Case models.Prior probability distributions for leading parameters are provided in Tables \@ref(tab:priors-base5ABCD) and \@ref(tab:priors-base3CD).

*TO DO: Move these tables to model description and refer to them here*


```{r priors-base5ABCD}

df <- data.frame(Parameter = c("ln M",
                     "Steepness",
                     "ln R0",
                     "Tau",
                     "Sig",
                     "q HSMSAS",
                     "ln q QCSS",
                     "ln q HSSS",
                     "q CPUE Hist",
                     "q CPUE 1996+"),
                 Distribution = c("Norm", "Beta", "Unif","Fixed","Fixed","Unif","Norm","Norm","Unif","Unif"),
                 p1 = c("ln(0.5)",
                        "5.83",
                        "1",
                        "0.8",
                        "0.2",
                        "0",
                        "ln(0.628 x 0.65)",
                        "ln(0.1869 x 0.35)",
                        "0",
                        "0"),
                 p2 = c("0.1",
                        "2.5",
                        "12",
                        "NA",
                        "NA",
                        "1",
                        "0.3",
                        "0.3",
                        "1",
                        "1"))
   knitr::kable(df, caption = "Prior probability distributions used for the Base Case 5ABCD model. Beta parameters for steepness give distribution with mean ~ 0.7 and sd ~ 0.15.", booktabs = TRUE, linesep = "")

```


```{r priors-base3CD}

df <- data.frame(Parameter = c("ln M",
                     "Steepness",
                     "ln R0",
                     "Tau",
                     "Sig",
                     "ln q WCVISS",
                     "q CPUE Hist",
                     "q CPUE 1996+",
                     "q Triennial"),
                 Distribution = c("Norm", "Beta", "Unif","Fixed","Fixed","Norm","Unif","Unif","Unif"),
                 p1 = c("ln(0.5)",
                        "5.83",
                        "1",
                        "0.8",
                        "0.2",
                        "ln(0.228)",
                        "0",
                        "0",
                        "0"),
                 p2 = c("0.1",
                        "2.5",
                        "12",
                        "NA",
                        "NA",
                        "0.3",
                        "1",
                        "1",
                        "1"))
   knitr::kable(df, caption = "Prior probability distributions used for the Base Case 3CD model. Beta parameters for steepness give distribution with mean ~ 0.7 and sd ~ 0.15.", booktabs = TRUE, linesep = "")

```

\clearpage

For both stocks, we tested sensitivity of the model outputs to the following data and assumptions:

- Inclusion of a year-location interaction as a random effect in the commercial CPUE data (historical period: pre-1996 and modern period: post-1995)
- Inclusion of commercial CPUE indices for the historical and modern periods.
- Inclusion of the NMFS Triennial Survey index for Area 3CD
- The prior probability distribution for $ln(q)$
- The prior probability distribution for $ln(M)$
- The prior probability distribution for steepness
- The assumption of knife-edged selectivity and maturity at age 2
- The updated growth parameters
- The assumed fixed value of observation error $\sigma_O$
- The assumed fixed value of $\sigma_R$
- The assumed fixed value of $\sigma_W$

Results are presented under these headings below, with Base Case parameter
settings provided in Table XX. In all sensitivity runs, posterior samples were
drawn systematically every 5,000 iterations from a chain of length 10
million, resulting in 2,000 posterior samples. The first 1,000 samples
were dropped to allow for sufficient burn-in.


## Sc 1b and Sc 1c. Exclusion of a year-location interaction as random effect in commercial CPUE indices
The base case models were fit to historical and modern commercial CPUE indices that included a year-location interaction as random effect (see model description and Appendix B). Two sensitivity analyses are shown to illustrate the effect of removing the interaction term from both indices (i.e., fitting the delay difference model to historical and modern CPUE indices calculated using equation \@ref(eq:cpuesens2)):

- \textbf{Sc 1b.} Use equations without the interaction term to create CPUE indices for historical and modern periods. Use the annual CVs resulting from the analysis as annual weighting terms in objective function of delay difference model (Equation TX.X).

- \textbf{Sc 1c.} Use equations without the interaction term to create CPUE indices for historical and modern periods. Double the annual CVs resulting from the analysis directly as weighting terms in objective function of delay difference model (Equation TX.X).

Sc 1c was done because the annual CVs of the CPUE indices were very small (less than 0.1 in some years). Annual CVs were doubled to addres concerns that the objective function of the delay difference model may be giving the CPUE indices too much weight when CVs were very small.

## Sc 1d. Exclusion of commercial CPUE index for the modern period

A sensitivity analysis was done where the modern CPUE index was removed from the model altogether. This was to address concerns that CPUE in the post-IVQ period (post-1995) may not be a good index of abundance, as some skippers reported avoiding Pacific Cod when quotas were low (@forrest2013). For comparison, to illustrate the effect of the historical CPUE index on model output, the historical CPUE index was removed. Finally, both commercial CPUE indexes were removed.

*TO DO: improve above text*

\begin{itemize}

\item[] \textbf{Sc 1d.} Remove modern CPUE index from the model. Historical index includes year-location interaction term as a random effect.
\item[] \textbf{Sc 1e.} Remove historical CPUE index from the model. Modern index includes year-location interaction term as a random effect.
\item[] \textbf{Sc 1f.} Remove both CPUE indices from the model.

\end{itemize}


## Sc 1e. Exclusion of the NMFS Triennial survey index for Area 3CD

A sensitivity analysis was done where the NMFS Triennial Survey index was removed from the model.

\begin{itemize}

\item[] \textbf{Sc 1g (Area 3CD only).} Remove NMFS Triennial Survey index from the model.

\end{itemize}


## Sc 2a and 2b. Prior probability distribution for $ln(q)$

For 5ABCD, two sensitivity analyses are shown to illustrate the effect of the normal prior probability distribution assumed for $ln(q)$ for the QCS and HS Synoptic Surveys:

\begin{itemize}

\item[] \textbf{Sc 2a.} The mean of the QCS Synoptic survey was set to the same mean as for the HS Synoptic survey, i.e., mean $ln(q)$ = $ln(0.186)$ .

\item[] \textbf{Sc 2b.} A uniform prior was used for \textit{q} for both the QCS and HS Synoptic Surveys.

\end{itemize}

For 3CD, two sensitivity analyses are shown to illustrate the effect of the normal prior probability distribution assumed for $ln(q)$ for the WCVI Synoptic Survey:

\begin{itemize}

\item[] \textbf{Sc 2a.} The sd of the WCVI Synoptic survey was set to the same sd as for the QCS and HS Synoptic surveys, i.e., sd = 0.3.

\item[] \textbf{Sc 2b.} A uniform prior was used for \textit{q} for the WCVI Synoptic Surveys.

\end{itemize}


## Sc 3a to 3c. Prior probability distribution for $ln(M)$

Three sensitivity analyses are shown to illustrate the effect of the
parameters of the normal prior distribution assumed for $ln(M)$:

\begin{itemize}

\item[] \textbf{Sc 3a.} The mean was held at the Base Case value of 0.5, while the standard
  deviation was increased to 0.2.
\item[] \textbf{Sc 3b.} The mean was reduced to 0.4 and the standard deviation was held at
  the Base Case value of 0.1.
\item[] \textbf{Sc 3c.} The mean was reduced to 0.4 and the standard deviation was increased
  to 0.2.

\end{itemize}

<!--

Respective median posterior estimates of M were:

- 0.323 y^-1^ XX
- 0.347 y^-1^ XX
- 0.300 y^-1^ XX

compared to the median posterior Base Case estimate of M = 0.393 y^-1^. It
therefore appears that the assumed prior probability distribution for natural
mortality does influence posterior estimates of M and that the prior used in
the Base Case model may have resulted in higher estimates of M than if a less
informative prior had been used. Convergence properties appeared to be poor
for Case 1, with large auto-correlation in several chains. However, convergence
properties for Cases 2 and 3 were the same or better than those obtained for
the Base Case model, particularly for Case 3 (not shown).

The biomass estimates that resulted from each sensitivity case are shown in
Figure XX. There was almost no discernible difference in recent biomass
estimates among scenarios for the three cases. However, there were large
differences in estimated historical biomasses, with historical biomasses
estimated to be smaller than for the Base Case in all three scenarios. Because
of this, estimates of current stock status relative to the USR and LRP were
different for these three sensitivity cases. We only show results for cases
2 and 3, which had much better convergence properties than case 1, in
Figure XX. Results show that the stock was estimated to be larger relative
to the historical averages as estimates of M declined.
-->

## Sc 4a and Sc 4b. Prior probability distribution for steepness

Two sensitivity analyses were done to illustrate the effect of the prior probability distribution assumed for steepness in the base case model:

\begin{itemize}

\item[] \textbf{Sc 4a.} Use a uniform prior for steepness bounded between 0.21 and 0.999.
\item[] \textbf{Sc 4b.} Use a beta prior for steepness with mean = 0.85 and sd = 0.75.

\end{itemize}

<!--
Biomass and parameter estimates are shown in Figures XX and XX, where it can be seen that there was
relatively little effect of the prior on steepness on posterior estimates of
biomass, although estimates in recent years were slightly lower (Figure XX).
The median posterior estimate of B0 was much larger than the maximum estimated
biomass in the time series, and the model showed poor convergence for most
parameters. The model's tendency to sample very low estimates of steepness with
this prior resulted in some very large estimates of $ln(R_0)$ and
$ln(R_{Avg\_init})$ (Figure XX). This result suggests that an informative
prior for steepness helped to improve model convergence properties without
having a very large influence on biomass estimates (Figure XX).
-->

## Sc 5a. The assumption of knife-edged selectivity and maturity at age 2

One sensitivity analysis was done to illustrate the effect of the assumption that fish recruit to the fishery, all surveys and mature at age 2 *y*:

- **Sc 5a.** Set $kage = 3 y$ and update Ford-Walford parameters accordingly

<!-- TODO: the following should be Markdown not LaTeX -->

TO DO: More explanatory text here referring to new maturity estimates. Possibly add "ageless" catch-age model sensitvity separating maturity and selectivity at age 3 and age 2 respectively (but would still be assuming knife-edged so maybe no point)

## Sc 5b. Updated growth parameters
One sensitivity analysis was done to illustrate the effect of updating the von Bertalanffy growth parameters using available age and length data (see Appendix XX).

\begin{itemize}

\item[] \textbf{Sc 5b.} Use von Bertalanffy growth parameters used in the previous stock assessment (@forrest2013)

\end{itemize}

TO DO: More explanatory text here

## Sc 6a - 6c. Assumed fixed value of observation error $\sigma_O$
In the Base Case, 0.2 was assumed to be an appropriate value for $\sigma_O$. Two sensitivity analyses were done that reduced this value:

\begin{itemize}

\item[] \textbf{Sc 6a.} Fix $\sigma_O$ = 0.1.
\item[] \textbf{Sc 6b.} Fix $\sigma_O$ = 0.15.
\item[] \textbf{Sc 6c.} Fix $\sigma_O$ = 0.25.

\end{itemize}


## Sc 6c. Assumed fixed value of process error $\sigma_R$

In the Base Case and in @forrest2013, 0.8 was assumed to be an appropriate
value for $\sigma_R$, as this stock appears to have had very variable
recruitment throughout the history of the fishery. One sensitivity
analysis was done to test the effect of increasing the assumed value of $\sigma_R$:

\begin{itemize}

\item[] \textbf{Sc 6d.} Fix $\sigma_R$ = 1.0

\end{itemize}

<!--
Resulting estimates of historical biomass are shown in Figure XX. As for the
steepness sensitivity test, there was very little discernible difference in
the estimated historical time series between the Base Case model and the two
sensitivity cases. The largest effects were seen in the estimates of $B_0$
(Figure XX), which showed much lower posterior estimates obtained with
$\sigma_R$ = 0.4; and much higher and uncertain posterior estimates with
$\sigma_R$ = 1.0 as a function of the increased recruitment variation.
-->

## Sc 7a. Assumed fixed value of $\sigma_W$

Problems with interpreting the mean weight data were discussed in Appendix XX.
These problems stem from changes over time in the sample sizes of different
categories of length data, i.e., sorted and unsorted categories. Concerns
about the use of the mean weight data were also recorded in the review of
the 2005 assessment [@fargo2005]. This issue was acknowledged by
@sinclair2005, who noted that the mean weight series was necessary for
estimation of model parameters but was down-weighted in the objective function.

Given the uncertainties in interpreting this time series and its potential
to provide direct information for scaling the population size, two sensitivity analysis was done to illustrate the effect of the fixed value of $\sigma_w$, which was fixed at 0.2 in the base case:

\begin{itemize}

\item[] \textbf{Sc 7a.} Fix $\sigma_w$ = 0.4
\item[] \textbf{Sc 7b.} Fix $\sigma_w$ = 0.15

\end{itemize}
