# INTRODUCTION

## STOCK STRUCTURE AND LIFE HISTORY

Pacific Cod (*Gadus macrocephalus*) is a relatively short-lived, fast-growing member of the family Gadidae. A common name in British Columbia (BC) is grey cod (or gray cod). Populations of Pacific Cod are distributed from California, throughout the waters of BC, Gulf of Alaska and the Bering Sea to Russia, Korea, Japan and China [@hart1973]. Maximum observed age in British Columbia is around 10-11 years [@westrheim1996, this document], while a maximum age of approximately 13 years has been reported for Alaskan stocks [@roberson2001]. Maximum length recorded in British Columbia is 100 cm [@hart1973], although some larger specimens have been observed in Alaska and Russia [@westrheim1996]. In recent Synoptic trawl surveys in BC, the maximum recorded length was 93 cm (Appendix A, Table \@ref(tab:length-biosamples-surv)). Pacific Cod are demersal spawners, with several studies reporting that spawning most likely occurs during February to March. A comprehensive review of the biology, life history and distribution of Pacific Cod in BC is provided by @westrheim1996.

Four stocks of Pacific Cod are defined for management purposes on the BC coast: Strait of Georgia (4B); West Coast Vancouver Island (3CD); Queen Charlotte Sound (5AB); and Hecate Strait (5CD). This study focuses on the populations in Queen Charlotte Sound combined with Hecate Strait (5ABCD), and the West Coast Vancouver Island (3CD) (Figure XX).

Recent genetic analyses have identified a distinction between North American and Asian Pacific Cod populations, and have shown some evidence for distinction between Alaskan populations and those south of Dixon Entrance in British Columbia (reviewed in @forrest2013). There is also evidence that fish taken off the coast of Washington and the west coast of Vancouver Island may be distinct from fish sampled within the Strait of Georgia or Puget Sound. However, linkages, if any, among stocks in BC and those in Alaska remain poorly understood. To date it is uncertain whether genetic population structure exists within BC waters [@forrest2013]. Genetic samples have been collected from spawning grounds in Hecate Strait and Queen Charlotte Sound since the 2013 assessment but these have not yet been analysed.

The choice to provide science advice for combined areas 5AB and 5CD into a single assessment was due in part to poor model diagnostics and lack of historical fishery-independent indices of abundance for Area 5AB (@forrest2013), and in part due to lack of evidence for genetic distinction between the stocks. Provision of science advice for Areas 5ABCD combined should not imply that the Areas should be managed as a single area, which is a choice for fishery managers in consultation with fishing industry members and other interested parties.

## ECOSYSTEM CONSIDERATIONS

Population dynamics of Pacific Cod in BC have been characterized by large estimated variations in abundance [e.g., @sinclair2001; @forrest2013], although the causes are not clear. Hypotheses for apparent cyclic abundance in Hecate Strait include predator-prey cycles [@walters1986], density-dependent growth and mortality [@fournier1983],and northward water transport of larvae [@tyler1986; @tyler1991]. Natural mortality has been estimated as high as 0.6 - 0.65 *y*^-1^ in some stock assessments [e.g., @fournier1983; @sinclair2005] although lower estimates (~0.4 *y*^-1^) have also been obtained [@sinclair2001; @forrest2013]. The combination of apparently volatile dynamics with short life span and high natural mortality suggests periods of over/under harvest could result if harvest strategies are not designed to be robust to these features. However, in the context of the BC integrated groundfish fishery, constraints imposed by quotas for other species can mean that single-species considerations alone do not always dictate the best harvest strategy.

### PREY AND PREDATORS

Pacific Cod are omnivores, eating a diet of mainly marine invertebrates, including amphipods, euphausiids, shrimp and crabs. At around 50-55 cm they also become piscivorous, with Pacific Sand Lance (*Ammodytes hexapterus*) and Pacific Herring (*Clupea pallasi*) becoming important components of the diet [@westrheim1996]. Juvenile Sablefish (*Anoplopoma fimbria*) and adult Pacific Hake (*Merluccius productus*) have also been reported in the diet of Pacific Cod off the west coast of Vancouver Island @ware1986. Pacific Cod have been reported in the diets of Pacific Halibut (*Hippoglossus stenolepis*), North Pacific Spiny Dogfish (*Squalus suckleyi*), sea birds, seals and sealions @westrheim1996.

@walters1986 demonstrated a Pacific Cod-Herring predator-prey interaction in Hecate Strait, in contrast to @ware1986. Simulation models developed by @walters1986 concluded that availability of Pacific Herring prey could be an important driver of Pacific Cod production in Hecate Strait, and, similarly, that Pacific Cod predation could be a significant driver of Pacific Herring abundance. These authors acknowledged that there are alternative hypotheses for cycles in abundance of Pacific Cod and Pacific Herring (e.g., environmental forcing; see below) and suggested that large-scale management experiments may be the only way to distinguish among competing hypotheses.

### ENVIRONMENT

Several studies have investigated linkages between recruitment and environmental indices for Pacific Cod in Hecate Strait (see @westrheim1996 for review). The dominant hypothesis is an inverse relationship between recruitment and northward  advection of larvae (@tyler1986; @tyler1991). Northward advection has been shown to be positively correlated with mean annual sea level at Prince Rupert during the spawning season, which in turn has been used as an explanatory variable for recruitment by a number of authors [@fournier1983]; [@sinclair2001]; @sinclair2005-2; @sinclair2005). However, recent updates of the analyses by @tyler1991 failed to find a continuing correlation between Prince Rupert Sea level and recruitment of Pacific Cod in Hecate Strait (R. Forrest, Pacific Biological Station, unpublished data).This could in part be due to low quotas (and therefore lower catches) since 2001, contributing to stock assessment estimates of lower recruitment in recent years [@forrest2013].

### OTHER SPECIES

Other species caught with Pacific Cod include Arrowtooth Flounder (*Atheresthes stomias*), Yellowtail Rockfish (*Sebastes flavidus*), Pacific Ocean Perch (*S. alutus*), Lingcod (*Ophiodon elongatus*), Silvergray Rockfish (*S. brevispinis*), English Sole (*Parophrys vetulus*) and Big Skate (*Raja binoculata*) [@forrest2013]. Vessels catching Pacific Cod must hold quota for all quota species encountered [@dfo2017]. Since 1996, there has been 100% at-sea observer coverage on commercial bottom trawl vessels in BC. At-sea releases are recorded by observers and counted against the vessel's quota, according to agreed-upon discard mortality rates.

## FISHERIES

Pacific Cod in BC are caught almost entirely in the groundfish bottom trawl fishery, which is part of BC's integrated groundfish fishery [@dfo2017]. Pacific Cod is one of the principal target species of the trawl fishery in Hecate Strait. Currently, the majority of the BC Pacific Cod catch is taken from in Hecate Strait (Area 5CD) (Figures \@ref(fig:fig-catch-5abcd) and \@ref(fig:fig-catch-3cd)).

Pacific Cod are distributed throughout Area 5CD at depths mainly less than 150 m. Pacific Cod density appears to be highest over the Two Peaks/Butterworth, White Rocks, Shell Ground, Reef Island, and Horseshoe fishing grounds [@forrest2013]. In Queen Charlotte Sound (Area 5AB), Pacific Cod are caught mainly off Cape Scott and Mexicana Banks, north of Vancouver Island, in Area 5A, and around the edge of Goose Island Bank in Area 5B  [@forrest2013]. The depth range of capture in 5ABCD ranges from around 60 - 100 m, with data showing a shift to deeper depths since 1996 (Appendix B, Figure \@ref(fig:cpue-depth-hists)). The transition to deeper fishing grounds partially reflects a larger proportion of catches coming from deeper waters in Queen Charlotte Sound in more recent years (\@ref(fig:fig-catch-5abcd),as well as general expansion into deeper water. Annual reported catches of Pacific Cod in both Hecate Strait and Queen Charlotte Sound have shown considerable variability since the beginning of the time series in 1956 (Figure \@ref(fig:fig-catch-5abcd)). The depth range of catches off West Coast Vancouver Island (Area 3CD) is similar to Area 5ABCD, with the majority of catch coming from 0-200 m depth zones (Appendix B, Figure \@ref(fig:cpue-depth-hists)). See @sinclair2001 for description of changes in historical depth ranges of the fishery. See also Appendix B. Historical catches in Area 3CD have shown a similarly variable pattern to Area 5ABCD (Figure \@ref(fig:fig-catch-3cd))

*TO DO: check catch numbers below once tables are in. These numbers include US and discards. Maybe delete these summaries*

In Area 5CD (Figure \@ref(fig:fig-catch-5abcd)), major peaks in catches occurred in 1958 (5,702 t), 1965 and 1966 (8,870 t and 9,156 t), 1979 (5,736 t), 1987 (9,542 t), and 1991 (7,747 t). These peak years may be contrasted with years of low catches in 1961 (1,528 t), 1970 and 1971 (1,188 t and 1,333 t), 1985 (1,053 t), and the minimum on record in 2001 (214 t). Reported catches have increased since 2001 to 701 t in 2012, although it should be noted that recent low catches are partially a result of lowered quotas in the early to mid-2000s. Catch was reported by USA vessels from 1956 to 1978. The estimated USA portion of the total catch was approximately 15% over these years (Table XX).

Major peaks in catches in Area 5AB occurred in 1957 (2,625 t), 1965 (1,983 t), 1972 and 1975 (2,415 t and 2,470 t), 1987 (3,209 t), and 1991 (2,206 t). Low catch years included 1961 (259 t), 1970 (278 t), 1983 (184 t), 2000 (67 t) and the lowest year on record 2008 (35 t). Significant catches were reported by USA vessels from 1956 to 1980. The estimated USA portion of the total catch was approximately 50% over these years (Table XX).

Major peaks in catches in Area 3CD occurred in ... XXX ... Low catch years included ...XXX ... and the lowest year on record was ... XXX ...Significant catches were reported by USA vessels from 1956 to 1980. The estimated USA portion of the total catch was approximately XX% over these years (Table XX).

Prior to the introduction of at-sea observer coverage in 1996, estimates of at-sea releases (discards) for the period 1956-1995 were obtained from fishing logbooks. These estimates are considered an underestimate of the actual releases (Table XX). Estimates in years following the introduction of 100% at-sea observer coverage in 1996 can be considered to be  accurate. Since 1996, the proportions of estimated discards have been considerably higher than in years before at-sea observers (Tables XX and XX ... landings, discards, usa), especially in Queen Charlotte Sound, largely as a result of reduced total catches and TACs (Table XX ... TACs). Pacific Cod can be legally discarded by trawlers in BC. However, on-board observers first estimate the quantity being discarded. This is assigned a discard mortality rate which is counted against the vessel's Pacific Cod quota. Therefore, in addition to greater accuracy in reporting of discards since 1996, incentives to avoid discarding have also been greater.

Japanese and Soviet vessels also trawled in waters off BC in the late 1960s and early 1970s. These vessels were mainly targeting rockfish and likely at depths greater than 150 m. The bycatch of Pacific Cod in these fisheries is, however, unknown. Given uncertainty in foreign catches and discards in the earlier parts of the time series, total catch estimates should be considered underestimates prior to 1996.

Bottom trawl fishing effort has been somewhat cyclic in all areas, especially in Hecate Strait [@forrest2013]. Total effort of all trawl vessels has declined in all areas in recent years. A detailed analysis of catch per unit effort (CPUE) is provided in Appendix B. As noted by @sinclair2000, there are a number of problems with the use of commercial catch per unit effort as an index of biomass for Pacific Cod. Changes in the management regime from an unrestricted fishery prior to 1992, to the introduction of TACs (1992-1996) and then to Individual Vessel Quotas (IVQs) (1997-present), as well as several increases in mesh size (@forrest2013, their Table 5), have affected the underlying relationship between commercial CPUE and abundance, and the relationship between fishing effort and fishing mortality. In recent years of lower Pacific Cod quotas (Table XX), many fishing masters report actively avoiding Pacific Cod to prevent their Pacific Cod quota being exceeded before catching available quotas for other species. In the present assessment CPUE series are split into pre- and post-1996 series, and general linear mixed models are used to attempt to standardize the indices (Appendix B).

## ASSESSMENT HISTORY

A number of methods have been used to assess Pacific Cod in Hecate Strait since the 1980s. @fournier1983 developed an age-structured model and used it to test for evidence of age-dependent trends in natural mortality, density-dependent natural mortality and catchability, and also for evidence of an environmental factor affecting recruitment. Evidence was found for a relationship between mean sea level at Prince Rupert and recruitment, and also for density-dependent natural mortality. Natural mortality was estimated to be 0.65 y-1 by @fournier1983. This author cautioned about the possibility of confounding among model parameters and systematic data biases that could influence conclusions from the analysis. Estimates of age were obtained from length-frequency analysis [@foucher1982].

Pacific Cod are one of the most difficult Pacific groundfish species to age. Annual rings (annuli) in otoliths, other bony structures and scales are difficult to distinguish from interannual growth checks (@beamish1981; @chilton1982; @roberson2001; @johnston2012). In British Columbia, age compositions have been estimated using length-based approaches, scales, otoliths and, currently, dorsal fin ray sections, although all methods present difficulties. In the absence of reliable direct age data, length-based approaches were used to assess the Hecate Strait stock during the 1990s [@haist1998; 1996; 1997; 1998]. The last of these assessments [@haist1998] suggested that the stock had reached an historic low in 1996, followed by a slight rebound.

@sinclair2000 used a simple surplus production model fit to a commercial CPUE index to assess the Area 5CD stock in 2000. This author cited significant structural changes in the fishery during the 1990s resulting in changes in quality and comparability of fishery-dependent data available for the analysis. Changes included voluntary increases in mesh size in the commercial fishery and introduction of individual vessel quotas (IVQs) in 1997 as discussed above. Given the large structural differences between the previous length-based models and the surplus production model, @sinclair2000 noted that results were remarkably comparable until 1994, with three estimated peaks in abundance occurring in 1965, 1974-5 and 1986-7. The two approaches diverged significantly after 1994, with the the length-based Multifan model [@haist1998] estimating an increase in biomass while the surplus production model estimated a decline. The differences were interpreted to be due to differences in the indices of abundance used to tune the models, as well as structural model differences.

@sinclair2001 developed a delay-difference model [@deriso1980; @schnute1985] containing a Ricker stock-recruit function to assess Pacific Cod in Areas 3CD and 5CD. Recruitment was assumed to be knife-edged at age 2 years. A report card summary of information available for the stock was also developed. The delay difference model provided a better statistical fit to the data than the previously-applied surplus production model [@sinclair2000]. However, biomass estimates followed a similar trend and magnitude.The 2001 Area 3CD stock was updated in 2002 [@Starr2002], using the same delay-difference model developed the previous year [@sinclair2001] and adding data from DFO's shrimp trawl survey. The authors of the 2002 assessment noted that the estimated MSY-based reference points /*F*_MSY/ and /*B*_MSY/ were not well estimated [@Starr2002].

The Area 5CD assessment was updated in 2004 [@sinclair2005], using a similar delay difference model to that used by @sinclair2001. Model fits were presented with alternative combinations of fixing or estimating natural mortality (*M*) and the steepness parameter of the stock-recruit function, *h* (Mace and Doonan 1988). They reported similar fits and biomass estimates for both scenarios but noted very different estimates of equilibrium MSY-based management parameters under alternative combinations of fixed and estimated *h* and *M*. They proposed "history-based" reference points, based on estimated historical biomass and fishing mortality, due to unreliability of MSY-based reference points.  The Area 5AB and 5CD stocks were last assessed in 2013 [@forrest2013] using a new delay difference model with a Beverton-Holt stock-recruit function and the assumption of knife-edged selectivity at 2 y. The model had some minor structural differences from the previous assessment, although bridging analyses showed these to have a relatively minor effect [@forrest2013, their Appendix A]. The 2013 assessment adopted the same historical reference points that had been used in 2004 and these were accepted during peer review for Area 5CD [@dfo2015]. However, no reference points were accepted for Area 5AB [@dfo2015-2]. Key uncertainties of noted by @forrest2013 were:

1. Uncertainty in fixed variance parameters, particularly the assumed observation error in the surveys, and the objective function component of the fit to annual mean weights;
2. Reliability of commercial CPUE as an index of abundance, and effects on CPUE of management changes post-1996;
3. Uncertainty in the prior probability distribution used for natural mortality *M*;
4. Uncertainty in the growth function (model parameters and assumptions of stationarity);
5. The possibility of violating the assumption of knife-edged recruitment at age 2 years, given evidence for younger fish in the length composition data from the commercial fishery; and
6. Uncertainty in stock structure.

Sensitivity to the first three of these uncertainties was partially addressed in @forrest2013 through the presentation of sensitivity analyses and alternative "model-averaged" decision tables for Areas 5AB and 5CD. The fourth and fifth uncertainties are partially addressed in the current assessment through the addition of extra sensitivity analyses comparing the previous and updated growth parameters, and comparing results with the assumption of knife-edged selectivity (Section \@ref(sensitivity-analyses). The sixth is still a key uncertainty for Pacific Cod. In the current assessment, data from Areas 5AB and 5CD are combined, under the assumption that Pacific Cod in Queen Charlotte Sound and Hecate Strait are a single stock.

# DATA SOURCES

## DATABASES
Data were extracted from a number of different databases:

**GFBio**
Biological samples and research cruise database. Groundfish Section, Marine
Ecosystems and Aquaculture Division, Science Branch, Fisheries and Oceans Canada,
Pacific Biological Station. This data archive includes most of the groundfish
specimen data collected since the 1950s. It therefore includes data from a variety
of sources (port and at-sea commercial sampling, research survey sampling),
collected using a variety of sampling methods.

**GFCatch**
Canadian trawl landings, 1954-1995 [@rutherford1999].

**PacHarvTrawl**
Canadian trawl landings, 1996 to March 31, 2007. SQL Server database, Groundfish Section, Marine Ecosystems and Aquaculture Division, Science Branch, Fisheries and Oceans Canada, Pacific Biological Station.

**GFFOS**
Canadian trawl landings, April 1, 2007 to 2018. View of the Fisheries and Oceans Canada (DFO) Fishery Operations (FOS) database. Groundfish Section, Marine Ecosystems and Aquaculture Division, Science Branch, Fisheries and Oceans Canada, Pacific Biological Station.

## CATCH DATA
Groundfish fisheries were managed by calendar year until 1996. Beginning in 1997-98 the fishing year changed to April 1--March 31. In 2010--2011 the fishing year was changed again to February 21 to February 20. Throughout this document, fishing years are defined as beginning on April 1 for all years, and are referenced by starting year, e.g., fishing year 1957 runs from April 1, 1957 to March 31, 1958. These definitions were used consistently in all calculations involving commercial catch data, including calculation of annual average mean weight in the catch (Appendix \@ref(analysis-of-biological-data)), and commercial CPUE (Appendix \@ref(commercial-cpue-standardization)). Landings data are presented
separately for Canada and the USA (Tables XX and XX). Combined USA-Canada landings data were obtained from the Pacific Marine Fisheries Commission reports for 1956-1981 and the USA landed portion was determined by subtracting the Canadian landed amount from the combined total for each year. In cases where
the difference was negative, the USA landed amount was set to zero (Tables XX and XX). Canadian data were obtained: from the GFCatch database for the period 1954-1995 [@rutherford1999]; from the PacHarvest database for the period 1996-March 31, 2007; and from the Fisheries and Oceans Canada (DFO) FOS
database for the period April 1, 2007 until the present. The annual size composition of commercial catches and landings were estimated from port samples and at-sea samples collected by observers archived in the GFBio database.

## INDICES OF ABUNDANCE
Stock assessment models in Area 5ABCD were fit to three fishery-independent survey indices (Hecate Strait Multispecies Assemblage Survey, Hecate Strait Synoptic Survey and Queen Charlotte Sound Synoptic Survey); and two commercial CPUE indices derived from commercial bottom trawl catch and effort data (pre-1996 and post-1995).


Stock assessment models in Area 3CD were fit to two fishery-independent survey indices (West Coast Vancouver Island Synoptic Survey and NMFS Triennial Survey in Canada) and two commercial CPUE indices derived from commercial bottom trawl catch and effort data (pre-1996 and post-1995).

The fishery-independent indices of abundance were developed using swept area analyses. Details are provided in Appendix \@ref(fishery-independent-indices-of-abundance).

The commercial CPUE indices were standardized standardized for depth, fishing locality, month, vessel, and latitude, when available, using generalized linear mixed models (GLMMs), based on a Tweedie distribution. Details are provided in Appendix \@ref(commercial-cpue-standardization).

## BIOLOGICAL DATA
Updates to estimated growth, maturity, annual mean weights in commercial catches, and probabilistic distributions of length-at-age are provided in Appendix \@ref(analysis-of-biological-data).

*TO DO: probably need to say a little more here*

# STOCK ASSESSMENT MODEL

All models presented in this document are Bayesian models implemented in AD Model Builder [@fournier2012]. The models are based on the Integrated Statistical Catch Age Model (iSCAM), first reported in @martell2011. A number of modifications have been made to the code from its original version by the authors of this assessment to include delay difference calculations. The model in its present formulation is fully described in Appendix \@ref(delay-difference-model). Two major differences between the current model and the previous assessment [@forrest2013] are:

1. The current model estimates only one average recruitment parameter (/*R*_0/). The models in @forrest2013 and @martell2011 estimated three average recruitment parameters (1. /*R*_0/, average unfished recruitment used in derivation of stock-recruit parameters; 2. /*R*_init/ initial average recruitment used to initialise the age structure in the first year; and 3. /*R*_avg/ average recruitment for the time series). The decision to use just one average recruitment parameter was made because there is little to no information for estimating three parameters in the delay difference model, which contains no explicit age composition information.

2. The von Bertalanffy growth parameters have been updated in the current assessment for both stocks, to reflect more recent age and length data. Details are provided in Appendix (\@ref(analysis-of-biological-data)).

The reference models for the Area 5ABCD and 3CD asessments are discussed in more detail in Section (\@ref(base-case-models)).

# REFERENCE POINTS AND HARVEST CONTROL RULE

The DFO Fishery Decision-making Framework Incorporating the Precautionary Approach (PA) policy [@dfo2009] requires stock status to be characterized using three reference points:

- A Reference Removal Rate;
- A Limit Reference Point (LRP);
- An Upper Stock Reference point (USR).

In the current assessment, these reference points are incorporated into the decision tables (Section  \@ref(decision-tables)), where projected probabilities of breaching the reference points are reported, i.e., they are not incorporated into a formal harvest control rule.

Provisional values of $USR = 0.8B_{MSY}$ and $LRP = 0.4B_{MSY}$ are suggested in the absence of stock-specific reference points [@dfo2009]. The framework specifies a limit reference removal rate of $F_{MSY}$. We refer to the reference removal rate as the limit removal rate (LRR) throughout this
document. The PA policy also endorses “history-based” proxies based on estimated average spawning biomass and fishing mortality over a productive historical period [@dfo2009].

As already noted, large uncertainties in the productivity parameters *M* and *h* have resulted
in substantial uncertainties in MSY-based reference points for Hecate Strait Pacific Cod in previous assessments [@Starr2002; @sinclair2005; @forrest2013]. Given uncertainty in productivity parameters for this stock, @sinclair2005 suggested using alternative reference points based on the reconstructed history of the stock, i.e., "history-based" reference points. They recommended the Limit Reference Point to be the minimum spawning biomass from which the stock recovered to above average levels. This was estimated to have occurred in 1971 (i.e., $LRP = B_{1971}$). @sinclair2005 suggested long-term average Biomass ($B_{Avg}$) as a candidate proxy Upper Stock Reference and long-term average harvest rate ($U_{Avg}$) as a proxy for the reference removal rate.

@sinclair2005 and @forrest2013 acknowledged that the absolute estimate of biomass in 1971 is dependent on model formulation, but found that most model formulations agreed that 1971 was the year in which the stock was lowest and subsequently recovered to above average levels. Therefore, they recommended the LRP be set at $B_{1971}$ estimated by the assessment model, rather than the absolute 1971 biomass estimated in their specific stock assessment. The Groundfish Subcommittee of PSARC [@fargo2005] subsequently recommended the use of $B_{1971}$ as the LRP for the Hecate Strait stock and it was again acepted as LRP by a Regional Peer Review (RPR) process in 2014 [@dfo2015]. Concurrently, long-term average Biomass ($B_{Avg}$) between 1956 and 2004, and long-term average fishing mortality ($F_{Avg}$) for the same period were accepted by the RPR for the USR and LRR, respectively [@dfo2015].

While there was no precedent for reference points in Queen Charlotte Sound, the minimum stock size from which the biomass was estimated to have recovered to an above average level occurred in 1985 [@forrest2013]. These authors proposed $B_{1985}$ as the LRP for the Queen Charlotte Sound, with average biomass and fishing mortality for the period 1956-2004 as the USR and LRR, respectively. However, no reference points were accepted at the RPR for Queen Charlotte Sound [@dfo2015-2]. The main reason cited was that the fishery in Area 5AB had essentially become an "avoidance" fishery for Pacifc Cod (to avoid breaching the Pacific Cod TAC before TACs for other groundfish species had been realised). Therefore the RPR participants felt that post-1996 estimates of abundance, which were largely informed by low catches, could not be assumed to accurately reflect abundance.

@forrest2018 simulation-tested a set of alternative reference points for Hecate Strait Pacific Cod and Rock Sole (*Lepidopsetta* spp.). They found that the "history-based" reference points (or operational control points, OCPs) that had been used for Pacific Cod in 2013 [@forrest2013] were robust to stock assessment biases because they scaled in the same direction as bias in estimates of biomass and fishing mortality. However, they were not necessarily good proxies for MSY-based reference points and tended to produce more precautionary catch recommendations than reference points based on $B_{MSY}$, $B_{0}$ and the spawning potential ratio (SPR; @clark1991). While the "history-based" reference points outperformed others in terms of long-term conservation outcomes, there were sometimes large trade-offs in terms of catch and catch stability [@forrest2018]. Reference points based on estimated $B_{0}$ performed similarly to the "history-based" reference points but tended to have better trade-off properties [@forrest2018].

In the absence of accepted reference points for Area 5AB, we suggest that some of the model concerns with the 5AB model may have been addressed by combining data for Areas 5AB and 5CD in the present stock assessment. Therefore we suggest using the same reference points for Area 5ABCD as had been used for Area 5CD in [@forrest2013]. In the absence of accepted reference points for Area 3CD, we suggest the same. Suggested reference points are provided in Table \@ref(tab:suggested-ref-points). In addition to the LRR, LRP and USR discussed above, two benchmark measures are also included: (i) $F_{2018}$ and (ii) $B_{2019}$. These will be used in the decision tables to show whether: (i) fishing mortality is projected to increase or decrease under alternative 2018 projected catch levels; and whether biomass is projected to increase or decrease under alternative 2018 projected catch levels.

The list of performance measures that will be used in decision tables for the Pacific Cod stocks in Hecate Strait and Queen Charlotte Sound (Area 5ABCD) is given in Table XX. Biomass-based performance measures were calculated as projected 2019 biomass relative to reference points, under alternative 2018 projected catch levels. Fishing mortality-based performance measures were calculated as projected 2018 fishing mortality relative to the reference points, under alternative 2018 projected catch levels. We do not currently present alternative reference points in this assessment (e.g., reference points based $B_{0}$), but suggest these could be explored for these stocks.

*TO DO: Move this table to Tables section when it is made*

```{r suggested-ref-points}

df <- data.frame(Reference_point = c("Bmin",
                     "Bavg",
                     "Favg",
                     "B2019",
                     "F2018"),
                 Definition = c(
                   "Minimum biomass from which the stock recovered to above average level. Area 5ABCD: Biomass in 1971; Area 3CD: Biomass in 1986",
                   "Average biomass for the period 1956-2004",
                   "Average fishing mortality for the period 1956-2004",
                   "Projected biomass in 2019",
                   "Projected fishing mortality in 2018"),
                 Role = c("LRP",
                        "USR",
                        "LRR",
                        "Benchmark",
                        "Benchmark")) 
   knitr::kable(df, caption = "List of reference points used for the Reference Case 5ABCD and 3CD models.", booktabs = TRUE, linesep = "")

```



# REFERENCE CASE MODELS

The Reference Case models for both areas 5ABCD and 3CD are XX.

## PRIOR PROBABILITY DISTRIBUTIONS

Prior probability distributions for the Area 5ABCD and 3CD Reference Case models
are shown in Figure XX and Table XX.

Broad, uniform prior probability distributions were used for $ln(R_0)$,
$ln(R_{Avg})$, $ln(R_{Avg\_init}$) and $ln(q_{CPUE}$), where the subscript
CPUE indicates the commercial CPUE data from 1956-1995. These uniform
distributions reflect our ignorance the scale of the population.

A Beta distribution was used for steepness with shape parameters that
resulted in a distribution with mean = 0.7 XX and SD = 0.15 XX. These parameter
choices resulted in a distribution with almost no probability density for
values less than 0.2 XX, implying that no transformation was necessary
(Figure XX). @sinclair2005 fixed steepness at 0.75 in one of their
"preferred" scenarios. In their other "preferred" scenario, the MPD estimate
of steepness was 0.53. The prior probability distribution chosen here
encompasses both of these values. A sensitivity analysis was done for
both areas with a uniform distribution for steepness between 0.21 XX and
0.99 XX, with very little impact on posterior estimates of biomass
(see below).

A normal distribution was used for $ln(M)$ with mean = $ln(0.5)$  XX
and SD = 0.1 XX. @sinclair2005 obtained MPD estimates of natural mortality
of 0.596 and 0.567 in their two "preferred" scenarios. The bridging
analysis provided in Appendix XX of this document suggested that natural
mortality could be considerably lower, depending on the values of other
fixed or estimated parameters. For the reference cases presented here, we chose
to centre the prior probability distribution a little lower than the MPD
values reported by @sinclair2005. Model sensitivity to both the mean and
the standard deviation of the distribution is presented below.

Normal distributions were used for $ln(q_{HSAS})$, $ln(q_{HSSS})$, and
$ln(q_{QSSS}$ where the subscripts $HSAS$, $HSSS$, and $QSSS$ indicate
the Hecate Strait Assemblage Survey, Hecate Strait Synoptic Survey, and
the Queen Charlotte Sound Synoptic Survey respectively (Table XX). Normal
distributions centred on $ln(1.0)$ were selected because the survey estimates
of biomass were derived from swept area analysis
(Eqs. \@ref(eq:sweptareabiomass)--\@ref(eq:sweptareacpue)) and could therefore
reasonably be expected to be some fraction of unity. A large standard
deviation was used to reflect ignorance of the scale of the swept area
analysis compared with the true biomass. Note there was no Assemblage Survey
in Queen Charlotte Sound (Area 5AB). Broad uniform distributions were used
for $ln(q_{CPUE})$, reflecting large uncertainty in the scale of the
relationship between commercial CPUE data and true biomass.

A total of XX model parameters were conditionally estimated in Area 5ABCD;
while XX parameters were estimated for Area 3CD, which had one fewer survey
q parameters (Table XX).

# RESULTS

## AREA 5ABCD: QUEEN CHARLOTTE SOUND AND HECATE STRAIT

The joint posterior distribution was numerically approximated using the
Markov Chain Monte Carlo routines built into AD Model Builder
[@fournier2012]. Posterior samples were drawn systematically every 50,000 XX
iterations from a chain of length 100 million XX, resulting in 2,000 XX
posterior samples (the first 1,000 XX samples were dropped to allow for
sufficient burn-in). Convergence was diagnosed using visual inspection of the
trace plots (Figure XX) and visual examination of autocorrelation in posterior
chains (Figure XX). Autocorrelation was minor for most parameters, except for
$ln(R_{Avg\_init}$), for which autocorrelation was quite strong. This likely
reflects lack of information in the data about this parameter. Overall, there
was no strong evidence for lack of convergence, although the model occasionally
estimated very large values for $ln(R_0)$, possibly because of this parameter
was confounded with steepness ($h$, Figure XX). Very high estimates of
$ln(R_0)$ were obtained when $h$ was estimated to be very low (Figure XX).
Survey catchability parameters were positively correlated with each other
and negatively correlated with $ln(M)$, implying that there is limited
information in the data to distinguish between a small productive population
or a larger, less productive population (Figure XX).

Maximum posterior density (MPD) model fits to the three indices of abundance
are shown in Figure XX. Model-estimated indices of abundance followed the
general trends of all three observed trends, although they failed to reach most
of the peaks in the respective datasets. As previously discussed above and in
the bridging analysis (Appendix XX), model outcomes, especially estimates of
productivity parameters, were very sensitive to the goodness of fit to the
indices of abundance, particularly peak commercial CPUE observations and the
2017 Synoptic Survey observation (Table XX). We consider the goodness of fit
to the indices of abundance to be a primary driver of uncertainty in this
assessment and present further sensitivity analyses in a later section.

Posterior probability distributions of estimated parameters are shown in
Figure XX. The median, 2.5^th^ percentile and 97.5^th^ percentile posterior
parameter estimates, and maximum posterior density (MPD) estimates, are given
in Table XX. With the exception of steepness, the posterior estimates did not
appear to be strongly influenced by the prior probability distributions. The
posterior probability distribution for steepness was very similar to the prior
probability distribution, implying that there is little information about this
parameter in the available data. Sensitivity to the prior distribution assumed
for steepness is tested in a later section. Posterior probability estimates of
$ln(M)$ tended to be lower than the prior values, although the right-hand tail
of the posterior distribution did overlap with the left-hand tail of the prior
distribution (Figure XX). We have already noted that posterior estimates of $M$
were strongly influenced by the fit to the index of abundance data (Table XX),
which likely has a stronger influence on estimates of $M$ than the prior
probability distribution.

Normal prior probability distributions were used for the log catchability
parameters $ln(q)$ for the Hecate Strait Assemblage and Synoptic Surveys
(Figure XX). These prior probability distributions did not appear to strongly
affect the posterior estimates, with the posterior distribution far to the left
of the prior distribution in both cases (Figure XX).

Spawning biomass is shown in Figure \@ref(fig:fig-base-biomass).

### REFERENCE POINTS

Posterior estimates of $F_{2017}$ and $B_{2018}$ are shown in Figures XX and
XX, and Table XX. Fishing mortality in 2017 was low compared to the historical
period, with the posterior median estimated to be 0.052y^-1^ XX.

## AREA 3CD: WEST COAST VANCOUVER ISLAND

Posterior samples were drawn systematically every 50,000 XX
iterations from a chain of length 100 million XX, resulting in 2,000 XX
posterior samples (the first 1,000 XX samples were dropped to allow for
sufficient burn-in). Convergence was diagnosed using visual inspection of the
trace plots (Figure XX) and visual examination of autocorrelation in posterior
chains (Figure XX).

### REFERENCE POINTS

Alternative reference points based on estimates of average historical biomass,
similar to those adopted in Area 5ABCD, were explored.

# SENSITIVITY ANALYSES

We present a number of sensitivity analyses to show the influence of certain data sources, fixed
parameters and prior probability distributions in the Area 5ABCD and 3CD Reference Case models.Prior probability distributions for leading parameters are provided in Tables \@ref(tab:priors-base5ABCD) and \@ref(tab:priors-base3CD).

*TO DO: Move these tables to model description and refer to them here*


```{r priors-base5ABCD}

df <- data.frame(Parameter = c("ln M",
                     "Steepness",
                     "ln R0",
                     "Tau",
                     "Sig",
                     "q HSMSAS",
                     "ln q QCSS",
                     "ln q HSSS",
                     "q CPUE Hist",
                     "q CPUE 1996+"),
                 Distribution = c("Norm", "Beta", "Unif","Fixed","Fixed","Unif","Norm","Norm","Unif","Unif"),
                 p1 = c("ln(0.5)",
                        "5.83",
                        "1",
                        "0.8",
                        "0.2",
                        "0",
                        "ln(0.628 x 0.65)",
                        "ln(0.1869 x 0.35)",
                        "0",
                        "0"),
                 p2 = c("0.1",
                        "2.5",
                        "12",
                        "NA",
                        "NA",
                        "1",
                        "0.3",
                        "0.3",
                        "1",
                        "1"))
   knitr::kable(df, caption = "Prior probability distributions used for the Reference Case 5ABCD model. Beta parameters for steepness give distribution with mean ~ 0.7 and sd ~ 0.15.", booktabs = TRUE, linesep = "")

```


```{r priors-base3CD}

df <- data.frame(Parameter = c("ln M",
                     "Steepness",
                     "ln R0",
                     "Tau",
                     "Sig",
                     "ln q WCVISS",
                     "q CPUE Hist",
                     "q CPUE 1996+",
                     "q Triennial"),
                 Distribution = c("Norm", "Beta", "Unif","Fixed","Fixed","Norm","Unif","Unif","Unif"),
                 p1 = c("ln(0.5)",
                        "5.83",
                        "1",
                        "0.8",
                        "0.2",
                        "ln(0.228)",
                        "0",
                        "0",
                        "0"),
                 p2 = c("0.1",
                        "2.5",
                        "12",
                        "NA",
                        "NA",
                        "0.3",
                        "1",
                        "1",
                        "1"))
   knitr::kable(df, caption = "Prior probability distributions used for the Reference Case 3CD model. Beta parameters for steepness give distribution with mean ~ 0.7 and sd ~ 0.15.", booktabs = TRUE, linesep = "")

```

\clearpage

For both stocks, we tested sensitivity of the model outputs to the following data and assumptions:

- Inclusion of a year-location interaction as a random effect in the commercial CPUE data (historical period: pre-1996 and modern period: post-1995)
- Inclusion of commercial CPUE indices for the historical and modern periods.
- Inclusion of the NMFS Triennial Survey index for Area 3CD
- The prior probability distribution for $ln(q)$
- The prior probability distribution for $ln(M)$
- The prior probability distribution for steepness
- The assumption of knife-edged selectivity and maturity at age 2
- The updated growth parameters
- The assumed fixed value of observation error $\sigma_O$
- The assumed fixed value of $\sigma_R$
- The assumed fixed value of $\sigma_W$

Results are presented under these headings below, with Reference Case parameter
settings provided in Table XX. In all sensitivity runs, posterior samples were
drawn systematically every 5,000 iterations from a chain of length 10
million, resulting in 2,000 posterior samples. The first 1,000 samples
were dropped to allow for sufficient burn-in.


## SC 1B AND SC 1C. EXCLUSION OF A YEAR-LOCATION INTERACTION AS RANDOM EFFECT IN COMMERCIAL CPUE INDICES
The reference case models were fit to historical and modern commercial CPUE indices that included a year-location interaction as random effect (see model description and Appendix B). Two sensitivity analyses are shown to illustrate the effect of removing the interaction term from both indices (i.e., fitting the delay difference model to historical and modern CPUE indices calculated using equation \@ref(eq:cpuesens2)):

- \textbf{Sc 1b.} Use equations without the interaction term to create CPUE
  indices for historical and modern periods. Use the annual CVs resulting from
  the analysis as annual weighting terms in objective function of delay
  difference model (Equation TX.X, Figure \@ref(fig:fig-sens1-biomass-5abcd)).

- \textbf{Sc 1c.} Use equations without the interaction term to create CPUE
  indices for historical and modern periods. Double the annual CVs resulting
  from the analysis directly as weighting terms in objective function of delay
  difference model (Equation TX.X, Figure \@ref(fig:fig-sens1-biomass-5abcd)).

Sc 1c was done because the annual CVs of the CPUE indices were very small (less than 0.1 in some years). Annual CVs were doubled to addres concerns that the objective function of the delay difference model may be giving the CPUE indices too much weight when CVs were very small.

## SC 1D. EXCLUSION OF COMMERCIAL CPUE INDEX FOR THE MODERN PERIOD

A sensitivity analysis was done where the modern CPUE index was removed from the model altogether. This was to address concerns that CPUE in the post-IVQ period (post-1995) may not be a good index of abundance, as some skippers reported avoiding Pacific Cod when quotas were low (@forrest2013). For comparison, to illustrate the effect of the historical CPUE index on model output, the historical CPUE index was removed. Finally, both commercial CPUE indexes were removed.

*TO DO: improve above text*

- \textbf{Sc 1d.} Remove modern CPUE index from the model. Historical
index includes year-location interaction term as a random effect, Figure \@ref(fig:fig-sens1-biomass-5abcd).
- \textbf{Sc 1e.} Remove historical CPUE index from the model. Modern
index includes year-location interaction term as a random effect, Figure \@ref(fig:fig-sens1-biomass-5abcd).
- \textbf{Sc 1f.} Remove both CPUE indices from the model, Figure \@ref(fig:fig-sens1-biomass-5abcd).

## SC 1E. EXCLUSION OF THE NMFS TRIENNIAL SURVEY INDEX FOR AREA 3CD

A sensitivity analysis was done where the NMFS Triennial Survey index was removed from the model.

- \textbf{Sc 1g (Area 3CD only).} Remove NMFS Triennial Survey index from the model, Figure \@ref(fig:fig-sens8-biomass-3cd).


## SC 2A AND 2B. PRIOR PROBABILITY DISTRIBUTION FOR $LN(Q)$

For 5ABCD, two sensitivity analyses are shown to illustrate the effect of the normal prior probability distribution assumed for $ln(q)$ for the QCS and HS Synoptic Surveys:

- \textbf{Sc 2a.} The mean of the QCS Synoptic survey was set to the same mean
- as for the HS Synoptic survey, i.e., mean $ln(q)$ = $ln(0.186)$, Figure \@ref(fig:fig-sens2-biomass-5abcd).
- \textbf{Sc 2b.} A uniform prior was used for \textit{q} for both the QCS and HS Synoptic Surveys, Figure \@ref(fig:fig-sens2-biomass-5abcd).

For 3CD, two sensitivity analyses are shown to illustrate the effect of the normal prior probability distribution assumed for $ln(q)$ for the WCVI Synoptic Survey:

- \textbf{Sc 2a.} The sd of the WCVI Synoptic survey was set to the same sd as for the QCS and HS Synoptic surveys, i.e., sd = 0.3, Figure \@ref(fig:fig-sens9-biomass-3cd).
- \textbf{Sc 2b.} A uniform prior was used for \textit{q} for the WCVI Synoptic Surveys, Figure \@ref(fig:fig-sens9-biomass-3cd).

## SC 3A TO 3C. PRIOR PROBABILITY DISTRIBUTION FOR $LN(M)$

Three sensitivity analyses are shown to illustrate the effect of the
parameters of the normal prior distribution assumed for $ln(M)$:

- \textbf{Sc 3a.} The mean was held at the Reference Case value of 0.5, while the standard
  deviation was increased to 0.2, Figures \@ref(fig:fig-sens3-biomass-5abcd) and
  \@ref(fig:fig-sens10-biomass-3cd).
- \textbf{Sc 3b.} The mean was reduced to 0.4 and the standard deviation was held at
  the Reference Case value of 0.1, Figures \@ref(fig:fig-sens3-biomass-5abcd) and
  \@ref(fig:fig-sens10-biomass-3cd).
- \textbf{Sc 3c.} The mean was reduced to 0.4 and the standard deviation was increased
  to 0.2, Figures \@ref(fig:fig-sens3-biomass-5abcd) and \@ref(fig:fig-sens10-biomass-3cd).

<!--

Respective median posterior estimates of M were:

- 0.323 y^-1^ XX
- 0.347 y^-1^ XX
- 0.300 y^-1^ XX

compared to the median posterior Reference Case estimate of M = 0.393 y^-1^. It
therefore appears that the assumed prior probability distribution for natural
mortality does influence posterior estimates of M and that the prior used in
the Reference Case model may have resulted in higher estimates of M than if a less
informative prior had been used. Convergence properties appeared to be poor
for Case 1, with large auto-correlation in several chains. However, convergence
properties for Cases 2 and 3 were the same or better than those obtained for
the Reference Case model, particularly for Case 3 (not shown).

The biomass estimates that resulted from each sensitivity case are shown in
Figure XX. There was almost no discernible difference in recent biomass
estimates among scenarios for the three cases. However, there were large
differences in estimated historical biomasses, with historical biomasses
estimated to be smaller than for the Reference Case in all three scenarios. Because
of this, estimates of current stock status relative to the USR and LRP were
different for these three sensitivity cases. We only show results for cases
2 and 3, which had much better convergence properties than case 1, in
Figure XX. Results show that the stock was estimated to be larger relative
to the historical averages as estimates of M declined.
-->

## SC 4A AND SC 4B. PRIOR PROBABILITY DISTRIBUTION FOR STEEPNESS

Two sensitivity analyses were done to illustrate the effect of the prior probability distribution assumed for steepness in the reference case model:

- \textbf{Sc 4a.} Use a uniform prior for steepness bounded between 0.21 and
- 0.999, Figures \@ref(fig:fig-sens4-biomass-5abcd) and \@ref(fig:fig-sens11-biomass-3cd).
- \textbf{Sc 4b.} Use a beta prior for steepness with mean = 0.85 and sd = 0.75, Figures \@ref(fig:fig-sens4-biomass-5abcd) and \@ref(fig:fig-sens11-biomass-3cd).

<!--
Biomass and parameter estimates are shown in Figures XX and XX, where it can be seen that there was
relatively little effect of the prior on steepness on posterior estimates of
biomass, although estimates in recent years were slightly lower (Figure XX).
The median posterior estimate of B0 was much larger than the maximum estimated
biomass in the time series, and the model showed poor convergence for most
parameters. The model's tendency to sample very low estimates of steepness with
this prior resulted in some very large estimates of $ln(R_0)$ and
$ln(R_{Avg\_init})$ (Figure XX). This result suggests that an informative
prior for steepness helped to improve model convergence properties without
having a very large influence on biomass estimates (Figure XX).
-->

## SC 5A. THE ASSUMPTION OF KNIFE-EDGED SELECTIVITY AND MATURITY AT AGE 2

One sensitivity analysis was done to illustrate the effect of the assumption that fish recruit to the fishery, all surveys and mature at age 2 *y*:

- **Sc 5a.** Set $kage = 3 y$ and update Ford-Walford parameters accordingly, Figures \@ref(fig:fig-sens5-biomass-5abcd) and \@ref(fig:fig-sens12-biomass-3cd).

TO DO: More explanatory text here referring to new maturity estimates. Possibly add "ageless" catch-age model sensitvity separating maturity and selectivity at age 3 and age 2 respectively (but would still be assuming knife-edged so maybe no point)

## SC 5B. UPDATED GROWTH PARAMETERS
One sensitivity analysis was done to illustrate the effect of updating the von Bertalanffy growth parameters using available age and length data (see Appendix XX).

- \textbf{Sc 5b.} Use von Bertalanffy growth parameters used in the previous stock assessment (@forrest2013), Figures \@ref(fig:fig-sens6-biomass-5abcd) and \@ref(fig:fig-sens13-biomass-3cd).

TO DO: More explanatory text here

## SC 6A - 6C. ASSUMED FIXED VALUE OF OBSERVATION ERROR $\sigma_O$
In the Reference Case, 0.2 was assumed to be an appropriate value for $\sigma_O$. Two sensitivity analyses were done that reduced this value:

- \textbf{Sc 6a.} Fix $\sigma_O$ = 0.1, Figures \@ref(fig:fig-sens6-biomass-5abcd) -- \@ref(fig:fig-sens6-index-cpue-post1995-5abcd), \@ref(fig:fig-sens13-biomass-3cd) -- \@ref(fig:fig-sens13-index-triennial-3cd), .
- \textbf{Sc 6b.} Fix $\sigma_O$ = 0.15, \@ref(fig:fig-sens6-biomass-5abcd) -- \@ref(fig:fig-sens6-index-cpue-post1995-5abcd), \@ref(fig:fig-sens13-biomass-3cd) -- \@ref(fig:fig-sens13-index-triennial-3cd)
- \textbf{Sc 6c.} Fix $\sigma_O$ = 0.25, \@ref(fig:fig-sens6-biomass-5abcd) -- \@ref(fig:fig-sens6-index-cpue-post1995-5abcd), \@ref(fig:fig-sens13-biomass-3cd) -- \@ref(fig:fig-sens13-index-triennial-3cd)

## SC 6C. ASSUMED FIXED VALUE OF PROCESS ERROR $\sigma_R$

In the Reference Case and in @forrest2013, 0.8 was assumed to be an appropriate
value for $\sigma_R$, as this stock appears to have had very variable
recruitment throughout the history of the fishery. One sensitivity
analysis was done to test the effect of increasing the assumed value of $\sigma_R$:

- \textbf{Sc 6d.} Fix $\sigma_R$ = 1.0, Figures \@ref(fig:fig-sens7-biomass-5abcd) and \@ref(fig:fig-sens14-biomass-3cd).

<!--
Resulting estimates of historical biomass are shown in Figure XX. As for the
steepness sensitivity test, there was very little discernible difference in
the estimated historical time series between the Reference Case model and the two
sensitivity cases. The largest effects were seen in the estimates of $B_0$
(Figure XX), which showed much lower posterior estimates obtained with
$\sigma_R$ = 0.4; and much higher and uncertain posterior estimates with
$\sigma_R$ = 1.0 as a function of the increased recruitment variation.
-->

## SC 7A. ASSUMED FIXED VALUE OF $\sigma_W$

Problems with interpreting the mean weight data were discussed in Appendix XX.
These problems stem from changes over time in the sample sizes of different
categories of length data, i.e., sorted and unsorted categories. Concerns
about the use of the mean weight data were also recorded in the review of
the 2005 assessment [@fargo2005]. This issue was acknowledged by
@sinclair2005, who noted that the mean weight series was necessary for
estimation of model parameters but was down-weighted in the objective function.

Given the uncertainties in interpreting this time series and its potential
to provide direct information for scaling the population size, two sensitivity analysis was done to illustrate the effect of the fixed value of $\sigma_w$, which was fixed at 0.2 in the reference case:

- \textbf{Sc 7a.} Fix $\sigma_w$ = 0.4, Figures \@ref(fig:fig-sens7-biomass-5abcd) and \@ref(fig:fig-sens14-biomass-3cd).
- \textbf{Sc 7b.} Fix $\sigma_w$ = 0.15, Figures \@ref(fig:fig-sens7-biomass-5abcd) and \@ref(fig:fig-sens14-biomass-3cd).


# DECISION TABLES
*TO DO: Update. This is 2014 text. Fix equations and dynamic references*

Performance measures were calculated over a sequence of alternative 2014 projected catch levels and are based on one-year projections to 2015.

Projected recruitment anomalies in 2015 were drawn randomly from a normal distribution, $\mathcal{N}\sim(0,\sigma_R)$.

Reference points and performance measures are listed in Tables 12 and 13.
The decision tables are designed to present probabilities of undesirable states under alternative 2014 projected catch levels.

An undesirable biomass-based performance measure occurs when 2015 projected biomass is below the reference point, i.e., $B_{2015}/B_\text{ReferencePoint} < 1$.
Probabilities using biomass-based reference points are only presented for Area 5CD for the reasons given above.

An undesirable fishing mortality-based performance measure occurs when projected 2014 fishing mortality is above the reference point, i.e., $F_{2014}/F_\text{ReferencePoint} > 1$.

Probabilities of undesirable states are measured as the proportion of burned-in posterior samples that meet criteria above (i.e., proportion of posterior samples < 1 for biomass-based performance measures; and proportion of posterior samples > 1 for fishing mortality-based performance measures). 

In the previous section, we identified some key sources of uncertainty in this assessment and suggested three solutions to presenting advice incorporating this uncertainty.
In both management Areas 5CD and 5AB, we suggested that we cannot further reduce the uncertainty arising from the prior probability distribution for ln($M$) (Figures 32 and 45); the goodness of fit to the mean weight data (Figures 36 and 47); or how well the model should fit to the commercial CPUE data, if at all (Figures 41, 44, 49 and 50).

In the following sections we present the Reference Case decision tables for each area, then present alternative ``model averaged'' decision tables that incorporate the uncertainty from the above sensitivity cases and Reference Cases.

The model averaging approach is described below.

We did not attempt to assign different weights to the alternative models in the construction of the model-averaged results.

## Reference case models

The decision table for the Area 5CD Reference Case model is provided in Table 26.
The probability of the 2015 biomass being below the 2014 biomass ranged from 12.4\% under no 2014 catch to 64.1\% under 2400 t, double the current TAC.

The probability of being below the LRP ranged from 12.3\% to 24.9\% over the range of catch levels considered.

The probability of being below the USR was higher and ranged from 51.2\% under no 2014 catch to 66.0\% over the range of catch levels considered.

The probability of the 2014 fishing mortality being greater than the 2013 fishing mortality ranged from 0.0\% to 100\%.

The probability of the 2014 fishing mortality being greater than the LRR ranged from 0.0\% to 33.9\%.
Estimated probabilities at the current TAC 1200 t are shown in bold (Table 26).

Under a 2014 catch level of 1200 t, there is an estimated 60\% probability that the 2015 biomass will be below the USR and an 18.2\% probability that the 2015 biomass will be below the LRP.


## Model Averaging

### Area 5CD: Hecate Strait

For Area 5CD, we present an alternative decision table with probabilities calculated from combined posterior estimates of performance measures from the following five models:
\begin{resdoclist}
\item Reference Case; 
\item the sensitivity case with prior probability distribution for ln($M$): $\mathcal{N}\sim(0.4,0.2)$;
\item the sensitivity case with $\sigma_W = 0.4$; 
\item the sensitivity case with $\sigma_0 = 0.15$; and 
\item the sensitivity case without commercial CPUE data.
\end{resdoclist}
We selected the sensitivity case for the prior on ln($M$) that had biomass estimates most divergent from the Reference Case model to better bracket the uncertainty due to this parameter.
Posterior estimates of biomass relative to the LRP and USR from each scenario are summarized in Figure 53. 

The vectors of 1,000 burned-in posterior samples from each of the five models, for each performance measure, under each alternative 2014 catch level, were combined into a single vector of 5,000 samples and probabilities of undesirable states (see above) were calculated from the combined samples. 

A similar approach was used in the 2011 assessment of Pacific Hake (Stewart et al. 2011), where two alternative stock assessment models were judged by the Pacific Fishery Management Council's Scientific and Statistical Committee to be equally plausible.
Another approach, based on Maximum Posterior Density model results, was used by Stewart et al. (2013) for the 2012 assessment of Pacific Halibut, where the magnitude of natural mortality was considered to be the primary axis of uncertainty.
A similar approach is being used for the 2013 assessment of Pacific Halibut, where three alternative, structurally different models, are being used to develop catch advice (Stewart and Martell. 2014).
The latter example draws from the ensemble modeling approach commonly used in weather forecasting (e.g., Hamill et al. 2012).

The ``Model-Averaged'' decision table probabilities for Area 5CD are presented in Table 28.
For most performance measures, probabilities were similar to those in the Reference Case model.
For example, the probability of B2015 < B2014 under a 2014 TAC of 1200 t was 39.6\% for the Reference Case model (Table 26), and 42.1\% from the averaged models (Table 28).
The probability of B2015 < LRP under a 2014 catch level of 1200 t  was 18.8\% for the averaged models, compared with 18.2\% for the Reference Case model.
The probability of B2015 < USR under a 2014 catch level of 1200 t was 59.8\% for the averaged models, compared with 60.0\% for the Reference Case model.


### Area 3CD: WEST COAST VANCOUVER ISLAND

## Summary

We presented the alternative, model averaged decision tables for Areas 5CD (Table 28) and 5AB (Table 29) in an attempt to more comprehensively incorporate substantial structural uncertainty in the assessments into advice for fishery managers and stakeholders.

However, we emphasize that there are major structural uncertainties that we have not been able to address in this assessment. These include, but are not limited to:
\begin{resdoclist}
\item The effects of the assumption of constant selectivity in the trawl fishery;
\item The effect of the assumption that recruitment to the fishery, surveys and the spawning biomass is knife-edged at age 2 years;
\item The impact of uncertainty in stock structure in understanding patterns in abundance; 
\item The impact of uncertainty in the magnitude of historical discarding and foreign catches;
\item The impact of change in onboard observer coverage and representativeness of length samples from the commercial catch.
\end{resdoclist}
Uncertainty is therefore under-represented in this assessment.

