# Commercial CPUE

```{r, knitr-opts-cpue, echo=FALSE, cache=FALSE}
knitr::opts_chunk$set(
  echo = TRUE
)
```

```{r}
library(dplyr)
library(ggplot2)
library(gfplot)
theme_set(theme_pbs())
```

```{r read-cpue-historic}
if (!file.exists(here::here("data/historic-cpue-raw-data.rds"))) {
  d <- gfplot::get_cpue_historic(species = NULL, end_year = 2017)
  readr::write_rds(d, here::here("data/historic-cpue-raw-data.rds"))
} else {
  d <- readr::read_rds(here::here("data/historic-cpue-raw-data.rds"))
}
```

We will start by removing all fishing events that have NAs for hours fished,
catch, or depth. We will also remove all fishing events that have hours fished,
catch, or depth less than zero.

```{r cpue-basic-filter}
# Basic filters that will apply to all data sets:
d <- d %>% filter(!is.na(hours_fished), !is.na(total), !is.na(best_depth_m),
    best_depth_m > 0, hours_fished > 0, total > 0, year >= 1956)
```

```{r cpue-historic-basic-filtering}
key_locality <- c(
  "cape scott spit",
  "mexicana",
  "topknot",
  "ne goose",
  "se goose",
  "nw goose",
  "sw goose",
  "reef island",
  "west horseshoe",
  "east horseshoe",
  "two peaks",
  "butterworth",
  "white rocks",
  "shell ground"
  )

# Suggested by Paul Starr by email in 2018:
new_locality_2018 <-
  c("triangle", "ole spot", "north moresby", "south bonilla", "west two peaks")

# Make sure we have spelled all the localities correctly:
stopifnot(all(key_locality %in% unique(d$locality_description)))
stopifnot(all(new_locality_2018 %in% unique(d$locality_description)))
```

We will reproduce the key localities analysis from REF. The key localities used
in that assessment were `r paste(key_locality, collapse = ", ")`. We will also
try including the additional localities `r paste(new_locality_2018, collapse = ", ")`.

The previous assessment used a depth threshold of 150m for the calculation of
commercial CPUE. A substantial portion of the Pacific Cod fishing events are at
depths deeper than 150m (Figure \@ref(fig:cpue-historic-depth)). Therefore, we
created a commercial CPUE data set with an alternative threshold of 350m to
encapsulate the vast majority of Pacific Cod fishing events.

```{r cpue-historic-depth}
# Look at the depth distribution:
filter(d, species_code == "222") %>%
  group_by(year, fishing_event_id, trip_id) %>%
  summarise(best_depth_m = best_depth_m[[1]]) %>%
  ggplot(aes(best_depth_m)) + geom_histogram(binwidth = 25) +
  geom_vline(xintercept = 150, lty = 2) +
  geom_vline(xintercept = 350, lty = 2) +
  scale_x_continuous(breaks = c(0, 150, 350, 500, 750), limits = c(0, 760)) +
  ylim(0, NA) +
  coord_cartesian(expand = FALSE) +
  theme_pbs()
```

```{r cpue-historic-data-binding}
# This is to create 3CD, 5AB, 5CD, and 5ABCD versions of the data:
d3cd <- filter(d, area %in% c("3CD"))
d5ab <- filter(d, area %in% c("5AB"))
d5cd <- filter(d, specific_area %in% c("5C", "5D"))
d5cd$area <- "5CD"
d5abcd <- bind_rows(d5ab, d5cd)
d5abcd$area <- "5ABCD"
d_all <- bind_rows(d3cd, d5ab, d5cd, d5abcd)
rm(d3cd, d5ab, d5cd, d5abcd)
```

```{r cpue-historic-calculations}
# A data set with the original key localities:
d_loc <- d_all %>%
  filter(locality_description %in% key_locality |
      (year <= 1967 & (specific_area == "5A" | specific_area == "5B")) |
      area == "3CD")

# This should match CPUE analysis D from the last research document:
d_resdoc_2015 <- d_loc %>%
  filter(best_depth_m <= 150) %>%
  group_by(year, area, trip_id, fishing_event_id) %>%
  summarise(
    pcod_catch = sum(ifelse(species_code == "222", total, 0)),
    effort = hours_fished[[1]]) %>%
  group_by(area, year) %>%
  summarise(pcod_catch = sum(pcod_catch), effort = sum(effort)) %>%
  mutate(cpue = pcod_catch / effort) %>%
  mutate(version = "Forrest et al. 2015 reconstruction")

# This version extends the depth filter to 300m, which encompasses most but
# not all Pacific Cod:
d_depth_350 <- d_loc %>%
  filter(best_depth_m <= 350) %>%
  group_by(year, area, trip_id, fishing_event_id) %>%
  summarise(
    pcod_catch = sum(ifelse(species_code == "222", total, 0)),
    effort = hours_fished[[1]]) %>%
  group_by(area, year) %>%
  summarise(pcod_catch = sum(pcod_catch), effort = sum(effort)) %>%
  mutate(cpue = pcod_catch / effort) %>%
  mutate(version = "Depth <= 350")

# This version adds in the key localities only:
d_depth_new_loc <- d_all %>%
  filter(locality_description %in% union(new_locality_2018, key_locality) |
      (year <= 1967 & (specific_area == "5A" | specific_area == "5B")) |
      area == "3CD") %>%
  filter(best_depth_m <= 150) %>%
  group_by(year, area, trip_id, fishing_event_id) %>%
  summarise(
    pcod_catch = sum(ifelse(species_code == "222", total, 0)),
    effort = hours_fished[[1]]) %>%
  group_by(area, year) %>%
  summarise(pcod_catch = sum(pcod_catch), effort = sum(effort)) %>%
  mutate(cpue = pcod_catch / effort) %>%
  mutate(version = "New localities")

# This version adds in the new key localities and new depth:
d_depth_350_new_loc <- d_all %>%
  filter(locality_description %in% union(new_locality_2018, key_locality) |
      (year <= 1967 & (specific_area == "5A" | specific_area == "5B")) |
      area == "3CD") %>%
  filter(best_depth_m <= 350) %>%
  group_by(year, area, trip_id, fishing_event_id) %>%
  summarise(
    pcod_catch = sum(ifelse(species_code == "222", total, 0)),
    effort = hours_fished[[1]]) %>%
  group_by(area, year) %>%
  summarise(pcod_catch = sum(pcod_catch), effort = sum(effort)) %>%
  mutate(cpue = pcod_catch / effort) %>%
  mutate(version = "Depth <= 350 & new localities")
```

We can see that our version of the commercial CPUE dataset that seeks to
replicate the last research document is nearly identical for some areas. We
believe it is slightly different in 5CD because we used the true fishing years
whereas the last research document used an old definition of fishing years for
consistency with a previous assessment. This version of commercial CPUE sums the catch
the Pacific Cod in each fishing year and divides that by the summed effort
across the entire bottom trawl fleet regardless of species caught or targeted.

```{r cpue-historic-paul, fig.cap="TODO"}
# The data from the last research document:
paul <- read.csv(here::here("data/cpue/Starr_2013_CPUE.csv"), stringsAsFactors = FALSE) %>%
  rename(year = FYear, area = Area, cpue = CPUE) %>%
  filter(Analysis == "AD") %>%
  select(-Analysis) %>%
  mutate(version = "Forrest et al. 2015")

# Compare:
bind_rows(d_resdoc_2015, paul) %>%
  ggplot(aes(year, cpue, colour = version)) +
  facet_wrap(~area) +
  geom_line() +
  theme_pbs() +
  ylab("CPUE (kg / hr)") +
  labs(colour = "Version") + xlab("")
```

When we compare the four versions of CPUE we created we see that adding the new
localities has a very minor effect and adding the deeper fishing events has
a moderate effect in all areas except 5CD (Figure
\@ref(fig:cpue-historic-bridging-plot)).

```{r cpue-historic-bridging-plot, fig.cap="TODO"}
# Plot all of the raw CPUE versions:
cpue_new <- bind_rows(
  d_depth_350,
  d_depth_new_loc,
  d_depth_350_new_loc
)
cpue_reconstructed <- d_resdoc_2015 %>%
  rename(cpue_reconstructed = cpue) %>%
  select(area, year, cpue_reconstructed)

left_join(cpue_new, cpue_reconstructed) %>%
  ggplot(aes(year, cpue, colour = version)) +
  facet_grid(
    factor(version, levels =
        c("New localities", "Depth <= 350",
          "Depth <= 350 & new localities"))~area) +
  geom_line() +
  geom_line(aes(y = cpue_reconstructed), lty = 2, col = "grey50") +
  theme_pbs() +
  guides(colour = FALSE) + xlab("") + ylab("CPUE (kg / hr)")
```

```{r save-cpue-data}
bind_rows(cpue_new, d_resdoc_2015) %>%
  saveRDS(file = here::here("data/pcod-cpue-bridging.rds"))
```

# Commercial CPUE index standardization

We can fit an index standardization model to account for the effects of depth,
month, and locality on the commercial CPUE times series. There are insufficient
older records with vessel and latitude associated with them to include them in
a model (Figure \@ref(fig:latitude-vessel-prop)).

```{r latitude-vessel-prop, fig.cap="TODO"}
# Can we use vessel and latitude?
g <- group_by(d_all, year, trip_id, fishing_event_id) %>%
  summarize(vessel = vessel[[1]]) %>%
  group_by(year) %>%
  summarise(prop_na = sum(is.na(vessel)) / n()) %>%
  ggplot(aes(year, prop_na)) + geom_point() +
  ylab("Proportion missing vessel ID") + xlab("")

g2 <- group_by(d_all, year, trip_id, fishing_event_id) %>%
  summarize(latitude = latitude[[1]]) %>%
  group_by(year) %>%
  summarise(prop_na = sum(is.na(latitude)) / n()) %>%
  ggplot(aes(year, prop_na)) + geom_point() +
  ylab("Proportion missing latitude") + xlab("")

cowplot::plot_grid(g, g2)
```

```{r, cpue-glmm-first-filter}
raw_dat <- d_all %>%
  filter(locality_description %in% union(new_locality_2018, key_locality) |
      (year <= 1967 & (specific_area == "5A" | specific_area == "5B")) |
      area == "3CD") %>%
  filter(best_depth_m <= 350) %>%
  filter(year <= 2017)

# Remove everything except for letters in the localities
# This makes it easier to plot the locality coefficients later:
raw_dat <-
  mutate(raw_dat, locality_desc = gsub(" ", "", locality_description)) %>%
  mutate(locality_desc = gsub("\\/", "", locality_desc)) %>%
  mutate(locality_desc = gsub("'", "", locality_desc)) %>%
  mutate(locality_desc = gsub(">", "", locality_desc)) %>%
  mutate(locality_desc = gsub("\\(", "", locality_desc)) %>%
  mutate(locality_desc = gsub("\\)", "", locality_desc)) %>%
  mutate(locality_desc = gsub("\\-", "", locality_desc)) %>%
  mutate(locality_desc = gsub("\\.", "", locality_desc)) %>%
  mutate(locality_desc = gsub("[0-9]", "", locality_desc))
```

After removing fishing events deeper than 350m and those that did not occur in the key Pacific Cod localities, we further removed fishing events that were missing a locality. This mostly occurs in the 1950s and early 1960s in area 5AB but only removes `r sum(is.na(raw_dat$locality_desc))` fishing events or `r round(100*sum(is.na(raw_dat$locality_desc)) / nrow(raw_dat), 2)`% of the total fishing events.

We then condensed the dataset down to create a column for Pacific Cod catch,
total hours fished, depth, month, and locality. However, prior to 1991, fishing
events were 'rolled up' into trips in the groundfish databases. We can clearly
see this in the data (Figure \@ref(fig:plot-effort-fe)). As a result, in order
to treat the timesseries consistently in the historical and recent decades, we
conducted the rest of our analysis on commercial CPUE at the trip level. To do
that we condensed the fishing event level data in 1991 and after into trips.
There is only ever a single locality and month in the database per trip, but
the depth has to be summarized in some way. We chose to summarize it as the
mean of the log depth. Furthermore, we removed all fishing events in 1991 and
after that were longer than six hours since these longer events are likely data
entry errors (see the red line after 1990 in (Figure
\@ref(fig:plot-effort-fe)).

```{r make-cpue-fe-data}
raw_dat <- filter(raw_dat, !is.na(locality_desc))

# Main dataset for model fitting:
out <- raw_dat %>% group_by(year, area, trip_id, fishing_event_id) %>%
  summarize(
    spp_catch = sum(ifelse(species_code == "222", total, 0)),
    hours_fished = hours_fished[[1]],
    depth = best_depth_m[[1]],
    month = month[[1]],
    locality = paste0("-", locality_desc[[1]]) # - is for formatting for easy coefficient plotting
  ) %>% ungroup()
```

```{r plot_pcod_dist, fig.cap="TODO"}
plot_pcod_dist <- function(dat, y, ylab = "", title = "") {
  ggplot(dat, aes_string("as.factor(year)", y = y)) + geom_boxplot() +
    scale_y_log10(breaks = c(0.1, 1, 10, 100, 1000, 10000), labels = scales::comma) +
    scale_x_discrete(breaks = seq(1950, 2030, 2)) +
    theme_pbs() +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5)) +
    facet_wrap(~area) + xlab("") + ylab(ylab) +
    ggtitle(title)
}
```

```{r plot-effort-fe, fig.cap="TODO"}
plot_pcod_dist(out, y = "hours_fished", ylab = "Effort (hr)",
  title = "Effort, all fishing events (trips in older years)") +
  geom_hline(yintercept = 6, col = "red")
out <- out %>%
  filter(year < 1991 | year >= 1991 & hours_fished <= 6)
```

```{r cpue-trip-dataset}
# Main dataset at the trip level:
out_trip <- out %>% group_by(year, area, trip_id) %>%
  summarize(
    spp_catch = sum(spp_catch),
    hours_fished = sum(hours_fished),
    depth = mean(depth),
    mean_log_depth = mean(log(depth)),
    month = month[[1]],
    locality = locality[[1]],
    n_month = length(unique(month)),
    n_locality = length(unique(locality))
  ) %>% ungroup()
stopifnot(all(out_trip$n_month == 1))
stopifnot(all(out_trip$n_locality == 1))
```

We can look at the distribution of catch, effort, and CPUE for this trip-level
dataset (Figure \@ref(fig:cpue-dist-plots)).

```{r cpue-dist-plots, fig.asp=3, fig.cap="TODO"}
g1 <- plot_pcod_dist(filter(out_trip, spp_catch > 0),
  y = "spp_catch",
  ylab = "Catch (kg)",
  title = "Catch, positive trips")

g2 <- plot_pcod_dist(filter(out_trip, spp_catch > 0),
  y = "hours_fished",
  ylab = "Effort (hours)",
  title = "Effort, positive trips")

g3 <- plot_pcod_dist(out_trip, y = "hours_fished",
  ylab = "Effort (hours)",
  title = "Effort, all trips")

g4 <- plot_pcod_dist(filter(out_trip, spp_catch > 0),
  y = "spp_catch/hours_fished",
  ylab = "CPUE (kg/hr)",
  title = "CPUE, positive trips")
cowplot::plot_grid(g1, g2, g3, g4, ncol = 1)
```

We can also look at the distribution of fished depth through time (Figure
\@ref(fig:depth-time-cpue)). We can see a deepening of the trawl fishing after
the early 1990s across all fishing trips and for just those fishing trips that
caught Pacific Cod.

```{r, depth-time-cpue, fig.cap="TODO"}
plot_pcod_dist(filter(out_trip, spp_catch > 0),
  y = "exp(mean_log_depth)",
  ylab = "Mean depth",
  title = "Mean depth, positive trips")

plot_pcod_dist(out_trip,
  y = "exp(mean_log_depth)",
  ylab = "Mean depth",
  title = "Mean depth, all trips")
```

We combined a number of localities with less than 100 total trips that caught
Pacific Cod through time into a single 'minor locality' category so that random
effects could be easily estimated for all localities. This is needed, despite
the above key localitys approach, because of the addition of 3CD and the
inclusion of all catch before 1967 in 5AB.

```{r, cpue-localities-b4-filter, fig.cap="Left is before filtering; right is after."}
depth_bands <- c(seq(0, 150, 25), 200, 350)
out_trip$year_factor <- as.factor(out_trip$year)
out_trip$month <- as.factor(out_trip$month)
out_trip$locality <- as.factor(out_trip$locality)
out_trip <- out_trip %>%
  mutate(pos_catch = ifelse(spp_catch > 0, 1, 0),
    depth_bin = gfplot:::factor_bin_clean(depth, depth_bands)
)

g1 <- group_by(out_trip, area, locality) %>%
  summarize(pos_catch_tot = sum(pos_catch)) %>%
  ggplot(aes(locality, pos_catch_tot)) + geom_col() +
  facet_wrap(~area, scales = "free") + coord_flip()

small_localities <- group_by(out_trip, area, locality) %>%
  summarize(pos_catch_tot = sum(pos_catch)) %>%
  filter(pos_catch_tot < 100) %>%
  arrange(area, -pos_catch_tot) %>%
  ungroup()

# small_localities %>%
#   knitr::kable(format = "pandoc")

out_trip <- mutate(out_trip, locality = as.character(locality)) %>%
  mutate(locality = ifelse(locality %in% small_localities$locality,
    "-minorlocality", locality)) %>%
  mutate(locality = as.factor(locality))

g2 <- group_by(out_trip, area, locality) %>%
  summarize(pos_catch_tot = sum(pos_catch)) %>%
  ggplot(aes(locality, pos_catch_tot)) + geom_col() +
  facet_wrap(~area, scales = "free") + coord_flip()

cowplot::plot_grid(g1, g2, ncol = 2)
```

We can also look at the catch by month and depth bin (Figure \@ref(fig:month-depth-catch)).

```{r month-depth-catch, fig.cap="Catch by month and depth bin."}
g1 <- group_by(out_trip, area, month) %>%
  summarise(catch = sum(spp_catch)) %>%
  ggplot(aes(month, catch)) + geom_point() + facet_wrap(~area)

g2 <- group_by(out_trip, area, depth_bin) %>%
  summarise(catch = sum(spp_catch)) %>%
  ggplot(aes(depth_bin, catch)) + geom_point() + facet_wrap(~area)

cowplot::plot_grid(g1, g2, ncol = 2)
```

We will fit a standardization model with a quadratic effect for depth and
random intercepts for month and locality.

```{r, standardize-depth}
mean_log_pcod_depth <- mean(filter(out_trip, pos_catch == 1)$mean_log_depth)
sd_log_pcod_depth <- sd(filter(out_trip, pos_catch == 1)$mean_log_depth)
# round(exp(mean_log_pcod_depth), 0)

out_trip <- mutate(out_trip,
  mean_log_depth_scaled = (mean_log_depth - mean_log_pcod_depth) / sd_log_pcod_depth,
  mean_log_depth_scaled2 = mean_log_depth_scaled^2
)
```

```{r, fit-glmm-models}
areas <- unique(out_trip$area)
formulas <- data_frame(formula = c(
  "year_factor",
  "year_factor + mean_log_depth_scaled + mean_log_depth_scaled2",
  "year_factor + (1 | locality)",
  "year_factor + (1 | month)",
  "year_factor + mean_log_depth_scaled + mean_log_depth_scaled2 + (1 | locality) + (1 | month)"),
  formula_version = c("Unstandardized", "+ Depth", "+ Locality", "+ Month",
    "Full standardization"))
torun <- expand.grid(formula = formulas$formula, area = areas, stringsAsFactors = FALSE)
torun <- inner_join(torun, formulas, by = "formula") # to get formula_version added

if (!file.exists(here::here("data/generated/cpue-models-re.rds"))) {
  library(doParallel)
  registerDoParallel(cores = floor(parallel::detectCores()/2L))
  m_re <- plyr::mlply(torun, function(formula, area, formula_version) {
    df <- out_trip[out_trip$area == area, , drop = FALSE]
    # message("Fitting area ", area, " and model ", formula)
    gfplot:::fit_cpue_index_re(df,
      formula_binomial = as.formula(paste("pos_catch ~", formula)),
      formula_lognormal = as.formula(paste("log(spp_catch / hours_fished) ~", formula)))
  }, .parallel = TRUE)
  readr::write_rds(m_re, here::here("data/generated/cpue-models-re.rds"))
} else {
  m_re <- readr::read_rds(here::here("data/generated/cpue-models-re.rds"))
}
predictions_re <- plyr::ldply(m_re, predict_cpue_index)
saveRDS(predictions_re,
  file = here::here("data/generated/cpue-re-predictions.rds"))
```

```{r plot-glmm-standardizations, fig.cap="TODO"}
unstandardized <- predictions_re %>%
  filter(formula_version == "Unstandardized") %>%
  rename(est_unstandardized = est, lwr_unstandardized = lwr, upr_unstandardized = upr) %>%
  select(year, area, model, est_unstandardized, lwr_unstandardized, upr_unstandardized)

plot_re_predictions <- function(model_version = "Combined") {
  predictions_re %>%
    filter(formula_version != "Unstandardized") %>%
    left_join(unstandardized, by = c("area", "year", "model")) %>%
    filter(model == model_version) %>%
    mutate(formula_version = gsub("\\+ ", " ", formula_version)) %>%
    mutate(formula_version =
        gsub("Full standardization", "All variables", formula_version)) %>%
    ggplot(aes(year, est, ymin = upr, ymax = lwr,
      fill = area)) +
    geom_line(aes(y = est_unstandardized), colour = "grey30", lty = 1) +
    ggplot2::geom_ribbon(
      aes(ymin = lwr_unstandardized, ymax = upr_unstandardized),
      fill = "#00000030") +
    ggplot2::geom_ribbon(alpha = 0.4) +
    geom_line(aes(colour = area)) +
    theme_pbs() +
    facet_grid(area~formula_version, scales = "free_y") +
    labs(y = "CPUE (kg/hour)", x = "") +
    ylim(0, NA) +
    geom_vline(xintercept = 1996, lty = 2, col = "grey60") +
    geom_vline(xintercept = 1991, lty = 2, col = "grey80") +
    guides(colour = FALSE, fill = FALSE) +
    ggtitle(model_version)
}
g_combined <- plot_re_predictions("Combined")
g_binomial <- plot_re_predictions("Binomial")
g_lognormal <- plot_re_predictions("Lognormal")
cowplot::plot_grid(g_combined, g_binomial, ncol = 1)
```

