\clearpage


```{r age-data}
d <- readRDS(file.path(rootd.data, "pcod-cache/pacific-cod.rds"))
```

```{r age-filter}
x <- filter(d$survey_samples,
  is.element(survey_abbrev, c("SYN HS", "SYN QCS","SYN WCVI")))
```

```{r length-temp, echo=FALSE, eval=TRUE}
xx <- d$commercial_samples %>%
  dplyr::filter(!is.na(length))

xx <- xx[!duplicated(xx$specimen_id), , drop = FALSE]
xx$area <- gfplot::assign_areas(xx$major_stat_area_name,
 area_regex = c("3[CD]+", "5[ABCD]+"))
```

```{r age-total_aged}
total_aged <- tidy_ages_raw(x,
  survey = c("SYN HS", "SYN QCS", "SYN WCVI"),
  ageing_method_codes = 6) %>%
  group_by(survey_abbrev, year) %>%
  summarise(n = total[1]) %>% ungroup() %>%
  summarise(n = sum(n)) %>% pull(n)
```


```{r length-total_lengths}
total_survey_lengths <- gfplot::tidy_lengths_raw(x,
                       survey = c("SYN HS", "SYN QCS", "SYN WCVI")) %>%
  group_by(survey_abbrev, year) %>%
  summarise(n = total[1]) %>% ungroup() %>%
  summarise(n = sum(n)) %>% pull(n)
```

# ANALYSIS OF BIOLOGICAL DATA

<!-- We extracted, manipulated, and plotted biological data using the R package gfplot (TODO-REF). -->

In this appendix we analyse length, maturity, and available ageing data to update growth and maturity parameters. We also plot age-frequency data derived from an age-length key to visualise the probable age composition in survey and commercial catch data.

## SYNOPTIC SURVEY DATA

We extracted length, weight and maturity data from the Hecate Strait, Queen Charlotte Sound, and West Coast Vancouver Island synoptic surveys from the GFBio database using the following criteria:

1. `SPECIES_CODE` = 222: Pacific Cod.

1. `TRIP_SUB_TYPE_CODE` = 2 or 3: research trips.

1. `SAMPLE_TYPE_CODE` = 1, 2, 6, 7, or 8: include only samples that are of type 'random' or 'total'.

1. `SPECIES_CATEGORY_CODE` = NULL, 1, 3, 5, 6, or 7: to eliminate samples sorted on unknown criteria.

1. `SAMPLE_SOURCE_CODE` = NULL, 1, 2: to extract sorted and unsorted samples but remove stomach content samples.

<!-- We extracted biological data using `gfplot::get_survey_samples()` and -->
<!-- `gfplot::get_commercial_samples()` for research survey and commercial samples, -->
<!-- respectively.  -->

<!-- We designated samples as one of three sample descriptions -->
<!-- based on combinations of two codes relating to sampling protocols: -->
<!-- `SPECIES_CATEGORY_CODE` and `SAMPLE_SOURCE_CODE`.  -->

<!-- Samples can be designated as 'unsorted samples' in which data were collected for -->
<!-- all specimens in the sample, or 'sorted samples' where specimens were sorted or -->
<!-- selected into 'keepers', which were sampled, and 'discards' which were not -->
<!-- sampled: -->

A summary of number of fish measured by year, survey and sex is provided in
Table \@ref(tab:length-biosamples-surv). Survey length-frequencies are shown in
Figure \@ref(fig:length-plotfrequencies-surv). A summary of number of fish
weighed by year, survey and sex is provided in Table
\@ref(tab:weight-biosamples). A summary of number of maturity records by year
and survey is provided in Table \@ref(tab:mat-biosamples).

```{r length-biosamples-surv, results='asis'}
x %>%
  filter(survey_abbrev %in% c("SYN HS", "SYN QCS", "SYN WCVI")) %>%
  filter(!is.na(length)) %>%
  group_by(survey_abbrev, year) %>%
  summarize(
    nlength_m = sum(sex == 1),
    nlength_f = sum(sex == 2),
    nlength_u = sum(sex == 0),
    maxlength_m = max(length[which(sex == 1)], na.rm=T),
    maxlength_f = max(length[which(sex == 2)], na.rm=T),
    maxlength_u = ifelse(nlength_u >0,  max(length[which(sex == 0)], na.rm=T),NA)
  ) %>%
  rename(
     Survey = survey_abbrev, Year = year, `N male` = nlength_m,
     `N female` = nlength_f, `N unsexed` = nlength_u, `Max male (cm)` = maxlength_m, `Max female (cm)` = maxlength_f, `Max unsexed (cm)` = maxlength_u) %>%
  knitr::kable(caption = "Number (N) of length measurements taken in the Hecate Strait (SYN HS), Queen Charlotte Sound (SYN QCS) and West Coast Vancouver Island (SYN WCVI) synoptic surveys", booktabs = TRUE, linesep = "", format = "pandoc")%>%
  kableExtra::kable_styling(latex_options = c("hold_position"), font_size = 9)
```

```{r weight-biosamples, results='asis'}
x %>%
  filter(survey_abbrev %in% c("SYN HS", "SYN QCS", "SYN WCVI")) %>%
  filter(!is.na(weight)) %>%
  group_by(survey_abbrev, year) %>%
  summarize(
    nweight_m = sum(sex == 1),
    nweight_f = sum(sex == 2),
    nweight_u = sum(sex == 0)

  ) %>%
  rename(
    Survey = survey_abbrev, Year = year, `N male` = nweight_m,
    `N female` = nweight_f, `N unsexed` = nweight_u) %>%
  knitr::kable(caption = "Number (N) of weight measurements taken in the Hecate Strait (SYN HS), Queen Charlotte Sound (SYN QCS) and West Coast Vancouver Island (SYN WCVI) synoptic surveys.", booktabs = TRUE, linesep = "", format = "pandoc")%>%
  kableExtra::kable_styling(font_size = 9)
```

```{r mat-biosamples, results='asis'}
x %>%
  filter(survey_abbrev %in% c("SYN HS", "SYN QCS", "SYN WCVI")) %>%
  filter(!is.na(maturity_code)) %>%
  filter(maturity_convention_code !=9) %>%   #filter out maturities not looked at
  group_by(survey_abbrev, year) %>%
  summarize(
    nmat_m = sum(sex == 1),
    nmat_f = sum(sex == 2)

  ) %>%
  rename(
    Survey = survey_abbrev, Year = year, `N male` = nmat_m,
    `N female` = nmat_f) %>%
  knitr::kable(caption = "Number (N) of maturities recorded in the Hecate Strait (SYN HS), Queen Charlotte Sound (SYN QCS) and West Coast Vancouver Island (SYN WCVI) synoptic surveys.", booktabs = TRUE, linesep = "", format = "pandoc")%>%
  kableExtra::kable_styling(font_size = 9)
```

```{r length-plotfrequencies-surv, fig.cap="Length-frequencies of Pacific Cod taken in the Hecate Strait (SYN HS), Queen Charlotte Sound (SYN QCS) and West Coast Vancouver Island (SYN WCVI) synoptic surveys. Note that for clarity only male and female specimens are plotted."}

 x %>%
  tidy_lengths_raw(survey = c("SYN HS", "SYN QCS", "SYN WCVI"),
  bin_size = 2,
  year_range = c(2002, Inf)) %>%
  plot_lengths()


```

\clearpage

## COMMERCIAL FISHERY DATA

We extracted length and weight data from commercial bottom trawl vessels from the GFBio database using the following criteria:

1. `SPECIES_CODE` = 222: Pacific Cod.

1. `TRIP_SUB_TYPE_CODE` = 1 or 4: 1 = non-observed domestic; 4 = observed domestic.

1. `GEAR_CODE` = 1: Bottom trawl.

1. `SAMPLE_TYPE_CODE` = 1, 2, 6, 7, or 8: include only samples that are of type 'random' or 'total'.

1. `SPECIES_CATEGORY_CODE` = NULL, 1, 3, 5, 6, or 7: to eliminate samples sorted on unknown criteria.

1. `SAMPLE_SOURCE_CODE` = NULL, 1, 2, 3: to extract sorted and unsorted samples but remove stomach content samples.

1. `SAMPLE_ID` not in 173726, 173740, 191471, 184243, 184159, 215903, or 223726: these samples were coded as Pacific Cod but have size composition inconsistent with the species. These samples were therefore excluded from further analysis.

1. Fishing year: April 1 to March 31 based on `trip_start_date`.

1. Quarter: months 4--6 = 1, months 7--9 = 2, months 10--12 = 3, months 1--3 = 4.

Summaries of number of fish measured by year, survey and sex are provided in Tables \@ref(tab:length-biosamples-com-5ABCD) and \@ref(tab:length-biosamples-com-3CD). Commercial length-frequencies are shown in Figure  \@ref(fig:length-plot-frequencies-com).

\clearpage

```{r length-biosamples-com-5ABCD, results='asis'}
xx %>%
  filter(area %in% c("5ABCD")) %>%
  filter(!is.na(length), year > 1955) %>%
  filter(year < 2018) %>%
  group_by(area, year) %>%
  summarize(
    nlength_m = sum(sex == 1),
    nlength_f = sum(sex == 2),
    nlength_u = sum(sex == 0)

  ) %>%
  rename(
    Area = area, Year = year, `N male` = nlength_m,
    `N female` = nlength_f, `N unsexed` = nlength_u ) %>%
  knitr::kable(caption = "Number (N) of length measurements taken in the commercial trawl fishery in Area 5ABCD.", booktabs = TRUE, format = "pandoc", linesep = "", longtable=TRUE)%>%
  kableExtra::kable_styling(latex_options = c("hold_position", "repeat_header"), font_size = 10)
```

\clearpage

```{r length-biosamples-com-3CD, results='asis'}
xx %>%
  filter(area %in% c("3CD")) %>%
  filter(!is.na(length), year > 1955) %>%
  filter(year < 2018) %>%
  group_by(area, year) %>%
  summarize(
    nlength_m = sum(sex == 1),
    nlength_f = sum(sex == 2),
    nlength_u = sum(sex == 0)

  ) %>%
  rename(
    Area = area, Year = year, `N male` = nlength_m,
    `N female` = nlength_f, `N unsexed` = nlength_u ) %>%
  knitr::kable(caption = "Number (N) of length measurements taken in the commercial trawl fishery in Area 3CD.", booktabs = TRUE, format = "pandoc", linesep = "", longtable=TRUE)%>%
  kableExtra::kable_styling(latex_options = c("hold_position", "repeat_header"), font_size = 10)
```

\clearpage

```{r length-plot-frequencies-com, fig.cap="Length-frequencies of Pacific Cod taken in the commercial trawl fishery. For clarity only lengths since 1996 are shown.", fig.asp=1.4}

xx %>%
 filter(!is.na(area)) %>%
 filter(year >= 1996) %>%
  filter(year < 2018) %>%
 filter(species_category_code %in% 1) %>%
 do(gfplot:::bin_lengths(., value = length, bin_size = 2)) %>%
 rename(length_bin = length) %>%
 group_by(year, length_bin, area) %>%
 summarise(n = n()) %>%
 group_by(year, area) %>%
 mutate(proportion = n / sum(n), total = sum(n)) %>%
 ungroup() %>%
 mutate(sex = "M", survey_abbrev = area) %>% # sex = "M" is a trick to plot them all
 plot_lengths() + xlab("Length (cm)") +
 guides(colour = FALSE, fill = FALSE)


```

\clearpage

## AGE SAMPLES

Pacific Cod are difficult to age due to inconsistency in annual marks, especially in the first few years of life [@beamish1981; @johnston2012; @kastelle2017]. A recent microchemistry-based validation study of Alaskan Pacific Cod otoliths revealed that visual aging of otoliths resulted in a high probability of over-ageing fish of ages 3--4 y. This was due to difficulty of readers distinguishing growth checks (translucent zones) from annuli [@kastelle2017]. Due to large difficulties in interpreting growth patterns on otoliths from BC Pacific Cod, they are here aged using dorsal finray sections, although this method is unvalidated [@beamish1981]. Ageing finray sections is resource intensive, since fins must be dried, sectioned and mounted in resin before reading. Therefore, production ageing of Pacific Cod has not been routinely done for BC populations.

A request was made in 2012 to age Pacific Cod from dorsal fin rays collected in recent Hecate Strait, Queen Charlotte Sound and West Coast Vancouver Island synoptic surveys. A total of `r total_aged` fin rays were aged, covering the years 2007, 2009, 2011 for SYN HS; 2011 for SYN QCS and 2006, 2008 and 2010 for SYN WCVI. A summary of number of fish aged by year, survey and sex is provided in Table \@ref(tab:age-biosamples). Proportions at each age are shown in Figure \@ref(fig:age-plotages). Due to the difficulties with interpreting annuli for Pacific Cod, a subset of fin rays were read by a second reader. There were 162 such secondary reads for Area 5CD and 57 for Area 3CD. Results showed that precision reads sometimes differed from the primary read by one or more years, particularly for older fish (Figure \@ref(fig:age-precision)).

Given the small ranges of years with aged fish, these data are insufficient to support an age-structured stock assessment model. However, they can be used to estimate growth and maturity parameters, and may be useful for visualizing probable age compositions in the commercial catch data.

\clearpage

```{r age-biosamples, results='asis'}
x %>%
  filter(survey_abbrev %in% c("SYN HS", "SYN QCS", "SYN WCVI")) %>%
  filter(!is.na(age)) %>%
  group_by(survey_abbrev, year) %>%
  summarize(
    nage_m = sum(sex == 1),
    nage_f = sum(sex == 2) #,
    #proportion_male = sprintf("%.2f", round(nage_m / (nage_f + nage_m), 2)),
    #proportion_female = sprintf("%.2f", round(nage_f / (nage_f + nage_m), 2))
  ) %>%
  rename(
    Survey = survey_abbrev, Year = year, `N male` = nage_m,
    `N female` = nage_f #,
    #`P male` = proportion_male,
    #`P female` = proportion_female
  ) %>%
  knitr::kable(caption = "Numbers (N) of otoliths aged in the Hecate Strait (SYN HS), Queen Charlotte Sound (SYN QCS) and West Coast Vancouver Island (SYN WCVI) synoptic surveys.", booktabs = TRUE, format = "pandoc", linesep = "")
```

```{r age-plotages, fig.cap="Proportions at age of fish aged in the Hecate Strait (SYN HS), Queen Charlotte Sound (SYN QCS) and West Coast Vancouver Island (SYN WCVI) synoptic surveys. Grey circles = males. Red circles = females."}
tidy_ages_raw(x,
  survey = c("SYN HS", "SYN QCS", "SYN WCVI"),
  ageing_method_codes = 6
) %>%
  plot_ages(
    count_label_size = 3, diagonal_lines = seq(-2100, -1850, 2),
    max_size = 12
  ) +
  scale_x_continuous(breaks = 2006:2011) +
  scale_y_continuous(breaks = seq(1, 10)) +
  ggtitle("") +
  ylim(0, NA)
```


```{r age-precision, fig.cap="Ageing precision for Pacific Cod. Each dot and cross-hatch represents an individual fish that has been aged twice. The x-axis represents the age and confidence interval recorded by the initial (primary) individual aging the fish. The y-axis represents the age and confidence interval recorded by the second (precision) individual aging the fish. The dashed diagonal line represents a perfect one-to-one agreement between the two ages. A small amount of random jitter has been added to both axes to reduce overplotting with the same jitter value added to both the x and y axes for a given fish.", fig.asp=1, out.width="3in", fig.width=4}
tidy_age_precision(d$age_precision, ageing_method_codes = 6) %>%
  plot_age_precision(n = 1e6) +
  scale_x_continuous(breaks = seq(0, 10, 1)) +
  scale_y_continuous(breaks = seq(0, 10, 1)) +
  ggtitle("")
```

\clearpage

## GROWTH PARAMETERS

Growth parameters were estimated by fitting the von Bertalanffy growth function to age and length data:

\begin{equation}
L_{s} = L_{\infty,s}\left( 1 - e^{- k_{s}\left( a_{s} - {a_{0}}_{s} \right)} \right)
 (\#eq:vB)
\end{equation}

where $L_{\infty,s}$, $k_{s}$ and ${a_{0}}_{s}$ are the parameters of the equation specific to sex, and $L_{s}$ and $a_{s}$ are paired length ($L$) and age ($a$) observations from synoptic surveys (Tables \@ref(tab:length-biosamples-surv) and \@ref(tab:age-biosamples)). We allowed for lognormal observation error.

The model was fit separately for males and females to: (a) all paired age-length samples; (b) Hecate Strait/Queen Charlotte Sound age-length samples; and (c) West Coast Vancouver Island age-length samples (Figures  \@ref(fig:vb-figs) and \@ref(fig:age-vb-pars); Table \@ref(tab:age-coeff-table)). Hecate Strait and Queen Charlotte Sound samples were combined because there was only one year of age observations (2011) for Queen Charlotte Sound (Table \@ref(tab:age-biosamples)). We sampled from the joint posterior distributions of each model with Stan [@carpenter2017; @rstan2018] using four chains and 2000 iterations per chain, discarding the first half of each as warmup. We placed uniform priors bounded at zero on $k$, $L_{\infty}$, and $\sigma$ (lognormal observation standard deviation), and a uniform prior on $a_0$.

\clearpage

```{r age-fit-vb, results='hide'}
surveys_list <- list(
  `SYN HS, SYN QCS, SYN WCVI` = c("SYN HS", "SYN QCS","SYN WCVI"),
  `SYN HS, SYN QCS` = c("SYN HS", "SYN QCS"),
  `SYN WCVI` = "SYN WCVI"
)

sexes <- c("male", "female")
vb_fits <-
  map(surveys_list, function(.survey) {
    map(sexes, function(.sex) {
      .dat <- filter(x, is.element(survey_abbrev, .survey))
      fit_vb(.dat, .sex, method = "mcmc", chains = 4L, iter = 2000L,
        uniform_priors = TRUE, seed = 1,
        cores = parallel::detectCores(),
        control = list(adapt_delta = 0.99, max_treedepth = 20L))
    })
  })
```

\clearpage

```{r age-coeff-table, results='asis'}
get_par_df <- function(.d, element = 1) {
  map_df(vb_fits, function(.x) {
    broom::tidyMCMC(.x[[element]]$model, conf.int = TRUE, conf.level = 0.95) %>%
    select(-std.error) %>%
    mutate(Surveys = paste(unique(.x[[element]]$data$survey_abbrev), collapse = ", ")) %>%
    mutate(Sex = paste(unique(.x[[element]]$data$survey_abbrev), collapse = ", ")) %>%
    mutate(Sex = sexes[element]) %>%
    filter(term != "sigma")
})}
get_par_df(vb_fits, 1) %>%
  bind_rows(get_par_df(vb_fits, 2)) %>%
  mutate(term = gsub("^k$", "$k$", term)) %>%
  mutate(term = gsub("^linf$", "$L_{\\\\infty}$", term)) %>%
  mutate(term = gsub("^t0$", "$a_0$", term)) %>%
  mutate(Sex = gsub("^male$", "Male", Sex)) %>%
  mutate(Sex = gsub("^female$", "Female", Sex)) %>%
  mutate(Surveys = factor(Surveys, levels = rev(names(surveys_list))))     %>%
  rename(Term = term, Estimate = estimate, Conf.low = conf.low, Conf.high = conf.high) %>%
  dplyr::select(Surveys,Sex,Term, Estimate, Conf.low, Conf.high) %>%
  mutate(Estimate = f(Estimate, 2),
    Conf.low = f(Conf.low, 2), Conf.high = f(Conf.high, 2)) %>%
  knitr::kable(
    caption = "von Bertalanffy growth coefficients for Pacific Cod in the Hecate Strait (SYN HS), Queen Charlotte Sound (SYN QCS) and West Coast Vancouver Island (SYN WCVI) synoptic surveys. Rows in bold represent values used in the models. Note that these values differ very slightly from those used in the models and described in the model appendix. The values in this table were run with extra chains and for more iterations with a higher Stan 'adapt delta' argument to more precisely explore the joint posterior. We plan to update the models with these values but, based on past model runs, expect it to make no qualitative difference.",
    booktabs = TRUE, linesep = "", escape=FALSE, format = "pandoc",
    align = c("l", "l", "l", "r", "r", "r")) %>%
  row_spec(seq(13, 18), bold = TRUE)
```

```{r vb-figs, fig.cap = "Length-age model fits. The length-age growth curve is a von Bertalanffy model. Female model fits are indicated as solid red lines and male model fits are indicated as dashed grey lines. Text on the panels shows the parameter estimates and light dots represent individual fish that the models are fit to.", fig.asp=0.3, fig.width=9, out.width="6.5in"}
vb_figs <- map(vb_fits, ~ plot_vb(
  object_male = .x[[1]], object_female = .x[[2]],
      col = c(Female = "red", Male = "grey40"), lab_x = 0.38) +
    ggtitle(paste(unique(.x[[1]]$data$survey_abbrev), collapse = ", ")))
cowplot::plot_grid(plotlist = vb_figs, nrow = 1)
```


```{r age-vb-pars, fig.asp=0.4, fig.cap = "Coefficient estimates from the von Bertalanffy model."}
get_par_df <- function(.d, element = 1) {
  map_df(vb_fits, function(.x) {
    broom::tidyMCMC(.x[[element]]$model, conf.int = TRUE, conf.level = 0.95) %>%
    select(-std.error) %>%
    mutate(surveys = paste(unique(.x[[element]]$data$survey_abbrev), collapse = ", ")) %>%
    mutate(Sex = paste(unique(.x[[element]]$data$survey_abbrev), collapse = ", ")) %>%
    mutate(Sex = sexes[element]) %>%
    filter(term != "sigma")
})}
get_par_df(vb_fits, 1) %>%
  bind_rows(get_par_df(vb_fits, 2)) %>%
  mutate(surveys = factor(surveys, levels = rev(names(surveys_list))))  %>%
  mutate(term = gsub("^t0$", "a_0", term)) %>%
  ggplot(aes(surveys, estimate, colour = Sex, ymin = conf.low, ymax = conf.high)) +
  geom_pointrange(position = position_dodge(width = 0.2)) +
  facet_wrap(~term, scales = "free_x") +
  coord_flip() +
  ylab("Parameter value") +
  xlab("") +
  theme_pbs() +
  scale_color_manual(values = c("female" = "red", "male" = "grey40"))

vbp <- get_par_df(vb_fits, 1) %>%
  bind_rows(get_par_df(vb_fits, 2))
vbp_wci_m <- filter(vbp, term == "k", surveys == "SYN WCVI", Sex == "male") %>% pull(estimate) %>% round(3)
vbp_wci_f <- filter(vbp, term == "k", surveys == "SYN WCVI", Sex == "female") %>% pull(estimate) %>% round(3)
vbp_hsqcs_m <- filter(vbp, term == "k", surveys == "SYN HS, SYN QCS", Sex == "male") %>% pull(estimate) %>% round(3)
vbp_hsqcs_f <- filter(vbp, term == "k", surveys == "SYN HS, SYN QCS", Sex == "female") %>% pull(estimate) %>% round(3)
vbp_all_m <- filter(vbp, term == "k", surveys == "SYN HS, SYN QCS, SYN WCVI", Sex == "male") %>% pull(estimate) %>% round(3)
vbp_all_f <- filter(vbp, term == "k", surveys == "SYN HS, SYN QCS, SYN WCVI", Sex == "female") %>% pull(estimate) %>% round(3)
```

Estimates of the von Bertalanffy growth rate $k$ were higher in the WCVI survey (male $k$ = `r vbp_wci_m` y^-1^; female $k$ = `r vbp_wci_f` y^-1^) compared to estimates of $k$ from the HS-QCS  surveys combined (male $k$ = `r vbp_hsqcs_m` y^-1^; female $k$ = `r vbp_hsqcs_f` y^-1^), and all surveys combined (male $k$ = `r vbp_all_m` y^-1^; female $k$ = `r vbp_all_f` y^-1^) (Table \@ref(tab:age-coeff-table)). The 2013 stock assessments for Hecate Strait and Queen Charlotte Sound [@forrest2013] used the same growth parameters that had been used in the 2004 assessment for Hecate Strait ($L_{\infty}$ = 89.48 cm; $k$ = 0.307 y^-1^ and $a_0$ = -0.116 y [@sinclair2005]). These values had been reported by @westrheim1996 for the WCVI stock, based on analyses of length-frequency data [@foucher1982]. @westrheim1996 had actually reported a lower growth rate for the Hecate Strait stock, i.e., $k$ = 0.203 y^-1^.

The current results for Hecate Strait (Table \@ref(tab:age-coeff-table)), are consistent with the parameters reported by @westrheim1996. This suggests that the growth rate use in the delay difference models in @forrest2013 and @sinclair2005 may have been too high for the Hecate Strait stock. The current Base Case models therefore uses the growth parameters reported for females in Table \@ref(tab:age-coeff-table), i.e., "SYN HS, SYN QCS" for Area 5ABCD; and "SYN WCVI" for the 3CD stocks.

\clearpage

Length-weight parameters (Equation \@ref(eq:weight-length)) were estimated using paired length and weight data from the synoptic surveys.

\begin{equation}
W_{s} = \alpha_{s}{L_{s}}^{\beta_{s}}
 (\#eq:weight-length)
\end{equation}

where $\alpha_s$ and $\beta_s$ are the parameters of the equation specific to sex, and $L_s$ and $W_s$ are paired length ($L$) and weight ($W$) observations from synoptic surveys (Tables  \@ref(tab:length-biosamples-surv) and \@ref(tab:weight-biosamples)). As for the growth parameters, Equation \@ref(eq:weight-length) was evaluated using data from all surveys combined; the HS-QCS  surveys combined; and the WCVI survey (Figures \@ref(fig:age-lw-figs) and \@ref(fig:age-lw-pars), Table \@ref(tab:lw-coeff-table)). The models were fit as robust linear regressions: $\ln(W_s) = \ln(a) + b \cdot \ln(L_s)$ with an M estimator [@venables2002]. Robust linear models were chosen over linear models with normally distributed error to downweight the influence of a small number of outlying specimens.

```{r age-fit-lw, results='hide'}
lw_fits <-
  map(surveys_list, function(.survey) {
    map(sexes, function(.sex) {
      .dat <- filter(x, is.element(survey_abbrev, .survey))
      fit_length_weight(.dat, .sex, method = "rlm")
    })
  })
```

```{r lw-coeff-table}
get_par_df <- function(.d, element = 1) {
  map_df(lw_fits, function(.x) {
    broom::tidy(.x[[element]]$model) %>%
    mutate(Surveys = paste(unique(.x[[element]]$data$survey_abbrev), collapse = ", ")) %>%
    mutate(Sex = paste(unique(.x[[element]]$data$survey_abbrev), collapse = ", ")) %>%
    mutate(Sex = sexes[element]) %>%
    filter(term != "statistic")
})}
get_par_df(lw_fits, 1) %>%
  bind_rows(get_par_df(lw_fits, 2)) %>%
  mutate(Conf.low = estimate - 1.96 * std.error, Conf.high = estimate + 1.96 * std.error) %>%
  mutate(Surveys = factor(Surveys, levels = rev(names(surveys_list)))) %>%
  mutate(term = gsub("\\(Intercept\\)", "$ln(\\\\alpha_s)$", term)) %>%
  mutate(term = gsub("log\\(length\\)", "$\\\\beta_s$", term)) %>%
  mutate(Sex = gsub("^male$", "Male", Sex)) %>%
  mutate(Sex = gsub("^female$", "Female", Sex)) %>%
  rename(Term = term, Estimate = estimate) %>%
  dplyr::select(Surveys,Sex,Term, Estimate, Conf.low, Conf.high) %>%
  knitr::kable(caption = "Length-weight coefficients for Pacific Cod in the Hecate Strait (SYN HS), Queen Charlotte Sound (SYN QCS) and West Coast Vancouver Island (SYN WCVI) synoptic surveys.", booktabs = TRUE, format = "pandoc", linesep = "", digits=2, escape=FALSE)
```

```{r age-lw-figs, fig.cap = "Length-weight model fits. Female model fits are indicated as solid red lines and male model fits are indicated as dashed grey lines. Text on the panels shows the parameter estimates and light dots represent individual fish that the models are fit to.", fig.asp=0.28, fig.width=9, out.width="6.5in"}
lw_figs <- map(lw_fits, ~ plot_length_weight(
  object_male = .x[[1]], object_female = .x[[2]],
      col = c(Female = "red", Male = "grey40"), lab_x_gap = 0.45) +
    ggtitle(paste(unique(.x[[1]]$data$survey_abbrev), collapse = ", ")))
cowplot::plot_grid(plotlist = lw_figs, nrow = 1)
```

```{r age-lw-pars, fig.asp=0.4, fig.cap = "Coefficients from the length-weight model fits."}
get_par_df <- function(.d, element = 1) {
  map_df(lw_fits, function(.x) {
    broom::tidy(.x[[element]]$model) %>%
    mutate(surveys = paste(unique(.x[[element]]$data$survey_abbrev), collapse = ", ")) %>%
    mutate(Sex = paste(unique(.x[[element]]$data$survey_abbrev), collapse = ", ")) %>%
    mutate(Sex = sexes[element]) %>%
    filter(term != "statistic")
})}
get_par_df(lw_fits, 1) %>%
  bind_rows(get_par_df(lw_fits, 2)) %>%
  mutate(conf.low = estimate - 1.96 * std.error, conf.high = estimate + 1.96 * std.error) %>%
  mutate(surveys = factor(surveys, levels = rev(names(surveys_list)))) %>%
  mutate(term = gsub("\\(Intercept\\)", "ln(a_s)", term)) %>%
  mutate(term = gsub("log\\(length\\)", "b_s", term)) %>%
  ggplot(aes(surveys, estimate, colour = Sex, ymin = conf.low, ymax = conf.high)) +
  geom_pointrange(position = position_dodge(width = 0.2)) +
  facet_wrap(~term, scales = "free_x") +
  coord_flip() +
  ylab("Parameter value") +
  xlab("") +
  theme_pbs() +
  scale_color_manual(values = c("female" = "red", "male" = "grey40"))
```

\clearpage

## MATURITY PARAMETERS

Maturity for Pacific Cod is assessed by visual inspection of the gonads, where maturity is assigned a code according to Gadid maturity stage.Fish are assessed as being in one of six states: 1.immature; 2.maturing; 3.mature (resting); 4.mature; 5.mature (spent); and 6.mature (ripe). For the purposes of fitting to a logistic curve, maturity was assigned a binary code, where fish with gonad maturity code 3 or higher were defined as mature (maturity assigned 1), and fish with gonad code 1 or 2 were defined as immature (maturity assigned 0).

We fit maturity ogives as logistic regressions of maturity (mature vs. not mature) against length or age:

\begin{align}
y_i &\sim \mathrm{Binomial}(\pi_i)\\
\mathrm{logit} \left( \pi_i \right) &= \beta_0 + \beta_1 x_i + \beta_2 F_i +  \beta_3 x_i F_i
 (\#eq:maturity)
\end{align}

where $y_i$ represents a 1 if fish $i$ is considered mature and a 0 if fish $i$
is considered immature. The $\beta$ parameters represent estimated coefficients,
$x_i$ represents the age of fish $i$, and $F_i$ represents
a binary predictor that is 1 if the fish is female and 0 if the fish is male.
The variable $\pi_i$ represents the expected probability of fish $i$ being
mature. We can then calculate of the age at 50% maturity as: $-(\log(1 / 0.5 - 1) + \beta_0) / \beta_1$ or $-(\log(1) + \beta_0) / \beta_1$ for males and $-(\log(1) + \beta_0 + \beta_2) / (\beta_1 + \beta_3)$ for females.

Estimated parameters are provided in Tables \@ref(tab:mat-fifty-tab) and \@ref(tab:age-mat-coefs-table), and Figure \@ref(fig:age-mat-coefs). Estimated maturity ogives are shown in Figure \@ref(fig:age-mat-figs).

Results suggest that age 3 y may be a more appropriate assumption for knife-edged maturity than age 2 y.

```{r age-fit-maturity}
surveys_list <- list(
  `SYN HS, SYN QCS, SYN WCVI` = c("SYN HS", "SYN QCS","SYN WCVI"),
  `SYN HS, SYN QCS` = c("SYN HS", "SYN QCS"),
  `SYN WCVI` = "SYN WCVI"
)
mat_fits <- map(surveys_list, function(.survey) {
  .dat <- filter(x, is.element(survey_abbrev, .survey))
  fit_mat_ogive(.dat, type = "age")
})
```

\clearpage

```{r age-mat-coefs-table, results='asis'}
mat_coefs <- plyr::ldply(mat_fits, function(.x) {
  broom::tidy(.x$model, conf.int = TRUE)
})

est <- group_by(mat_coefs, .id) %>%
  summarise(
    intercept_male = estimate[term == "(Intercept)"],
    intercept_female = estimate[term == "(Intercept)"] + estimate[term == "female"],
    slope_male = estimate[term == "age_or_length"],
    slope_female = estimate[term == "age_or_length"] +
    estimate[term == "age_or_length:female"]
  ) %>% reshape2::melt(variable.name = "term", value.name = "estimate")

combine_se <- function(se1, se2) {
  sqrt(se2^2 - se1^2)
}

se <- group_by(mat_coefs, .id) %>%
  summarise(
    intercept_male = std.error[term == "(Intercept)"],
    intercept_female = combine_se(std.error[term == "(Intercept)"],
      std.error[term == "female"]),
    slope_male = std.error[term == "age_or_length"],
    slope_female = combine_se(std.error[term == "age_or_length"],
      std.error[term == "age_or_length:female"])
  ) %>% reshape2::melt(variable.name = "term", value.name = "std.error")
inner_join(est, se) %>%
  mutate(.id = factor(.id, levels = names(surveys_list))) %>%
  mutate(term = gsub("^intercept_male$", "Intercept male: $\\\\beta_0$", term)) %>%
  mutate(term = gsub("^intercept_female$", "Intercept female: $\\\\beta_0 + \\\\beta_2$", term)) %>%
  mutate(term = gsub("^slope_female$", "Slope female: $\\\\beta_1 + \\\\beta_3$", term)) %>%
  mutate(term = gsub("^slope_male$", "Slope male: $\\\\beta_1$", term)) %>%
  mutate(Conf.low = estimate - 1.96 * std.error, Conf.high = estimate + 1.96 * std.error) %>%
  rename(Survey = .id, Term = term, Estimate = estimate) %>%
  dplyr::select(Survey,Term, Estimate, Conf.low, Conf.high) %>%
   knitr::kable(caption = "Coefficients from the logistic regression maturity ogives.",
     booktabs = TRUE, linesep = "", digits=2, format = "pandoc", escape=FALSE)
```

```{r mat-fifty-tab, results = 'asis'}
plyr::ldply(mat_fits, function(.x)
  data.frame(Female = .x$mat_perc$f.p0.5, Male = .x$mat_perc$m.p0.5)) %>%
  melt() %>%
  mutate(.id = factor(.id, levels = names(surveys_list))) %>%
  rename(Survey = .id, Sex = variable, `Estimated age-at-50% maturity` = value) %>%
  arrange(Survey, Sex) %>%
  knitr::kable(
    caption = "Estimates of age at 50\\% maturity from the logistic regression maturity ogives.", booktabs = TRUE, format = "pandoc", linesep = "", digits=1)
```

\clearpage

```{r age-mat-figs, fig.cap = "Age-at-maturity ogives. Maturity ogives are fit as logistic regressions to individual fish specimens, which are categorized as mature vs. not mature. The solid black lines represent fits to the female fish and the dashed gray lines represent fits to the male fish. The vertical lines indicate the estimated age or at length at 50\\% maturity. Text on the panels indicates the estimated age and length at 5, 50 and 95\\% maturity for females (F) and males (M). Short rug lines along the top and bottom of each panel represent up to 1500 randomly chosen individual fish with a small amount of random jittering to help differentiate individual fish.", fig.asp=1.7, fig.width=4.5, out.width="3.4in"}
mat_figs <- map(mat_fits, ~ plot_mat_ogive(.x) +
    coord_cartesian(xlim = c(0, 8.2), ylim = c(0, 1), expand = FALSE))
for (i in seq_along(mat_figs))
  mat_figs[[i]] <- mat_figs[[i]] + ggtitle(names(surveys_list)[i])
cowplot::plot_grid(plotlist = mat_figs, ncol = 1)
```

```{r age-mat-coefs, fig.pos = "H", fig.cap = "Rearranged coefficients from the logistic regression maturity ogives (e.g. intercept female = $\\beta_0 + \\beta_2$). Parameters are in logit or log odds space. The intercept refers to the log odds of maturity for a theoretical fish of age zero.", fig.width=6, out.width="4.5in"}
#based on outputs from age-mat-coefs-table
inner_join(est, se) %>%
  mutate(conf.low = estimate - 1.96 * std.error) %>%
  mutate(conf.high = estimate + 1.96 * std.error) %>%
  mutate(.id = factor(.id, levels = names(surveys_list))) %>%
  ggplot(aes(ymin = conf.low, ymax = conf.high, y = estimate,
    x = term, colour = .id)) +
  geom_pointrange(position = position_dodge(width = 0.4)) +
  coord_flip() +
  theme_pbs() +
  xlab("") + ylab("Coefficient") +
  labs(colour = "Survey group") +
  scale_color_brewer(palette = "Dark2")
```

\clearpage

## AVERAGE ANNUAL MEAN WEIGHT IN COMMERCIAL CATCH

The calculation of annual mean weight was done in the following steps. The same steps were used in both Areas 3CD and 5ABCD. The same length-weight relationship was use for all quarters, but differ by area. The values of the length-weight parameters used are for Area 3CD: `r paste0("$\\alpha = ", .ALPHA3, "$")` and `r paste0("$\\beta = ", .BETA3, "$")`; for Area 5ABCD: `r paste0("$\\alpha = ", .ALPHA, "$")` and `r paste0("$\\beta = ", .BETA, "$")`.

*Step 1.* Convert individual length ($l_i$) in each Sample ID ($j$) to weight ($w_i$):

\begin{equation}
{W_i} = a^q{L_i}^{b^q}
\end{equation}

where $a^q$ and $b^q$ are constant length-weight parameters.

*Step 2.* From the selected data set, calculate the mean weight ($W_j$) for each Sample ID ($j$):

\begin{equation}
{W_j} = \frac{{\sum\limits_{i=1}^{{N_j}} {{w_{i,j}}} }}{{{N_j}}}
\end{equation}

where $N_j$ is the number of weights $w_{ij}$ in Sample ID ($j$).

*Step 3.* The mean weight ($W_s$) for each sequential quarter was then calculated, weighted by the sample weight of Pacific Cod ($S_j$) in each SampleID ($j$). If the sample weight was recorded as data, it is used. Otherwise, the sum of the calculated weights from the sample is used:

\begin{equation}
{W_s} = \frac{{\sum\limits_{i=1}^{{K_s}} {{W_{j,s}S_{j,s}}}}}{{\sum\limits_{j=1}^{{K_s}} {{S_{j,s}}}}}
\end{equation}

where $K_j$ is the number of SampleIDs ($j$) in sequential quarter ($s$), where sequential quarter is a unique identifier for each quarter in the time series.

*Step 4.* The mean weight ($W_f$) for a fishing year was calculated by averaging the quarterly mean weight weighted by the commercial catch of Pacific Cod ($C_s$) during sequential quarter ($s$):

\begin{equation}
{W_f} = \frac{{\sum\limits_{s=1}^{{4}} {{W_sC_s}}}}{{\sum\limits_{s=1}^{{4}} {{C_s}}}}
\end{equation}

\clearpage
