\clearpage

# TABLES

```{r tab-catch-5abcd}
catch.table(catch.5,
            catch.5.discards,
            area = "5ABCD",
 cap = paste0("Reported catch (mt) of Pacific Cod in Area 5ABCD ",
              "by Canada and the USA, ",
              min(catch.5$year), "--", max(catch.5$year),
              ". The reported discards for the period ", min(catch.5$year),
              "--1995 are ",
              "unrepresentative of true discarding because the estimates were taken ",
              "from logbooks. Discard estimates since 1996 are based on at-sea ",
              "observations and are considered to be more representative of true discarding."))

```

\clearpage

```{r tab-catch-3cd}
catch.table(catch.3,
            catch.3.discards,
            area = "3CD",
 cap = paste0("Reported catch (mt) of Pacific Cod in Area 3CD ",
              "by Canada and the USA, ",
              min(catch.3$year), "--", max(catch.3$year),
              ". The reported discards for the period ", min(catch.3$year),
              "--1995 are ",
              "unrepresentative of true discarding because the estimates were taken ",
              "from logbooks. Discard estimates since 1996 are based on at-sea ",
              "observations and are considered to be more representative of true discarding."))
```

\clearpage

```{r tab-tac}
tac.table(tac,
 cap = paste0("Summary of TACs by area."))
```

\clearpage

```{r tab-priors-5abcd}
priors.table(base.model.5abcd,
basis.vec = c("Noninformative",
              "Informative-Previous assessment",
              "Informative-Previous assessment",
              "No prior-Fixed parameter",
              "No prior-Fixed parameter",
              "No prior-Fixed parameter",
              "No prior-Fixed parameter",
              "Noninformative-Technical necessity",
              "Noninformative-Technical necessity",
              "Noninformative-Technical necessity",
              "Noninformative-Technical necessity",
              "Noninformative-Technical necessity"),
             cap = paste0("Prior probability distributions, their parameters and initial values used in the ",
                          "Area 5ABCD Reference Case model. ", q.5abcd.desc))
```

\clearpage

```{r tab-priors-3cd}
priors.table(base.model.3cd,
basis.vec = c("Noninformative",
              "Informative-Previous assessment",
              "Informative-Previous assessment",
              "No prior-Fixed parameter",
              "No prior-Fixed parameter",
              "No prior-Fixed parameter",
              "No prior-Fixed parameter",
              "Noninformative-Technical necessity",
              "Noninformative-Technical necessity",
              "Noninformative-Technical necessity",
              "Noninformative-Technical necessity"),
             cap = paste0("Prior probability distributions, their parameters and initial values used in the ",
                          "Area 3CD Reference Case model. ", q.3cd.desc))
```

```{r tab-suggested-ref-points}
suggested.ref.points()
```

\clearpage

## MODEL RESULTS: AREA 5ABCD

```{r tab-param-table-5abcd, results='asis'}
make.parameters.table(base.model.5abcd,
  caption = paste0("Estimated and fixed parameters and prior probablilty distributions used ",
    "in the Reference Case, Area 5ABCD."),
  omit_pars = c("Log initial recruitment ($\\ln(\\overline{R}_{init})$)",
    "Log mean recruitment ($\\ln(\\overline{R})$)"),
  omit_selectivity_pars = TRUE)
```

```{r tab-param-est-table-5abcd, results='asis'}
pars_est_omit <- c("$\\overline{R}_{init}$", "$\\overline{R}$", "$\\vartheta$")
make.parameters.est.table(base.model.5abcd,
  caption = paste0("Posterior (2.5\\textsuperscript{th} percentile, Median, and ",
    "97.5\\textsuperscript{th} percentile) and MPD ",
    "estimates of key parameters from the Reference Case, Area 5ABCD. $R_0$ is in thousands of fish. $B_0$ is in tonnes. ",
    q.5abcd.desc),
  omit_pars = pars_est_omit)
```

```{r tab-ref-points-table-5abcd, results='asis'}
make.ref.points.table(base.model.5abcd,
                      omit_msy = TRUE,
                      add.hist.ref = TRUE,
                      lrp = c(2000, 2000),
                      usr = c(1956, 2004),
                      digits = 2,
                      caption = paste0("Posterior (2.5\\textsuperscript{th} percentile, Median, and ",
                                       "97.5\\textsuperscript{th} percentile) of reference points for Area 5ABCD. ",
                                       "Biomass is in tonnes."))
```

```{r tab-post-biomass-5abcd, results='asis'}
make.value.table(base.model.5abcd,
                 1,
                 digits = 0,
                 caption = paste0("Posterior (2.5\\textsuperscript{th} percentile, Median, and 97.5\\textsuperscript{th} ",
                                  "percentile) and MPD estimates of biomass (t) for the Reference Case, ",
                                  "Area 5ABCD."))
```

\clearpage

```{r tab-post-depl-5abcd}
make.value.table(base.model.5abcd,
                 5,
                 digits = 2,
                 caption = paste0("Posterior (2.5\\textsuperscript{th} percentile, Median, and 97.5\\textsuperscript{th} ",
                                  "percentile) and MPD estimates of biomass relative to $B_0$ ",
                                  "for the Reference Case, Area 5ABCD."))
```

\clearpage

```{r tab-post-recr-5abcd, results='asis'}
make.value.table(base.model.5abcd,
                 2,
                 digits = 0,
                 caption = paste0("Posterior (2.5\\textsuperscript{th} percentile, Median, and 97.5\\textsuperscript{th} ",
                                  "percentile) and MPD estimates of recruitment (thousands) for the Reference Case, ",
                                  "Area 5ABCD."))
```

\clearpage

```{r tab-post-f-5abcd, results='asis'}
make.value.table(base.model.5abcd,
                 3,
                 digits = 2,
                 caption = paste0("Posterior (2.5\\textsuperscript{th} percentile, Median, and 97.5\\textsuperscript{th} ",
                                  "percentile) and MPD estimates of fishing mortality, F, ",
                                  "for the Reference Case, Area 5ABCD."))
```

\clearpage

## MODEL RESULTS: AREA 3CD

```{r tab-param-table-3cd, results='asis'}
make.parameters.table(base.model.3cd,
  caption = paste0("Estimated and fixed parameters and prior probablilty distributions used ",
    "in the Reference Case, Area 3CD."),
  omit_pars = c("Log initial recruitment ($\\ln(\\overline{R}_{init})$)",
    "Log mean recruitment ($\\ln(\\overline{R})$)"),
  omit_selectivity_pars = TRUE)
```

```{r tab-param-est-table-3cd, results='asis'}
make.parameters.est.table(base.model.3cd,
  caption = paste0("Posterior (2.5\\textsuperscript{th} percentile, Median, and ",
    "97.5\\textsuperscript{th} percentile) and MPD ",
    "estimates of key parameters from the reference Case, Area 3CD. $R_0$ is in thousands of fish. $B_0$ is in tonnes.  ",
    q.3cd.desc),
  omit_pars = pars_est_omit)
```

```{r tab-ref-points-table-3cd, results='asis'}
make.ref.points.table(base.model.3cd,
                      omit_msy = TRUE,
                      add.hist.ref = TRUE,
                      lrp = c(1986, 1986),
                      usr = c(1956, 2004),
                      digits = 2,
                      caption = paste0("Posterior (2.5\\textsuperscript{th} percentile, Median, and ",
                                       "97.5\\textsuperscript{th} percentile) of reference points for Area 3CD. ",
                                       "Biomass is in tonnes."))
```

```{r tab-post-biomass-3cd, results='asis'}
make.value.table(base.model.3cd,
                 1,
                 digits = 0,
                 caption = paste0("Posterior (2.5\\textsuperscript{th} percentile, Median, and 97.5\\textsuperscript{th} ",
                                  "percentile) and MPD estimates of biomass (t) for ",
                                  "the Reference Case, Area 3CD."))
```

\clearpage

```{r tab-post-depl-3cd}
make.value.table(base.model.3cd,
                 5,
                 digits = 2,
                 caption = paste0("Posterior (2.5\\textsuperscript{th} percentile, Median, and 97.5\\textsuperscript{th} ",
                                  "percentile) and MPD estimates of biomass relative to $B_0$ ",
                                  "for the Reference Case, Area 3CD."))
```

\clearpage

```{r tab-post-recr-3cd, results='asis'}
make.value.table(base.model.3cd,
                 2,
                 digits = 0,
                 caption = paste0("Posterior (2.5\\textsuperscript{th} percentile, Median, and 97.5\\textsuperscript{th} ",
                                  "percentile) and MPD estimates of recruitment (thousands) for the Reference Case,",
                                  "Area 3CD."))
```

\clearpage

```{r tab-post-f-3cd, results='asis'}
make.value.table(base.model.3cd,
                 3,
                 digits = 2,
                 caption = paste0("Posterior (2.5\\textsuperscript{th} percentile, Median, and 97.5\\textsuperscript{th} ",
                                  "percentile) and MPD estimates of fishing mortality, F, ",
                                  "for the Reference Case, Area 3CD."))
```

\clearpage

## SELECTED SENSITIVITY RESULTS: AREA 5ABCD

```{r tab-param-table-sens2a-5abcd, results='asis'}
make.parameters.est.table(sens.models.2[[1]],
 caption = paste0("Posterior (2.5\\textsuperscript{th} percentile, Median, and ",
                   "97.5\\textsuperscript{th} percentile) and MPD ",
                   "estimates of key parameters ",
                  "for Sc 2a (mean of the QCS Synoptic Survey was set to the same mean as for the HS Synoptic Survey), Area 5ABCD. $R_0$ is in thousands of fish. $B_0$ is in tonnes. "),
  omit_pars = pars_est_omit)
```

```{r tab-param-table-sens2b-5abcd, results='asis'}
make.parameters.est.table(sens.models.2[[2]],
 caption = paste0("Posterior (2.5\\textsuperscript{th} percentile, Median, and ",
                   "97.5\\textsuperscript{th} percentile) and MPD ",
                   "estimates of key parameters ",
                  "for Sc 2b (uniform priors for synoptic survey catchability), Area 5ABCD. $R_0$ is in thousands of fish. $B_0$ is in tonnes. "),
  omit_pars = pars_est_omit)
```


```{r tab-param-table-sens3a-5abcd, results='asis'}
make.parameters.est.table(sens.models.3[[1]],
 caption = paste0("Posterior (2.5\\textsuperscript{th} percentile, Median, and ",
                   "97.5\\textsuperscript{th} percentile) and MPD ",
                   "estimates of key parameters ",
                  "for Sc 3a (mean ln(M)=ln(0.5), SD=0.2), Area 5ABCD. $R_0$ is in thousands of fish. $B_0$ is in tonnes. "),
  omit_pars = pars_est_omit)
```

\clearpage


```{r tab-param-table-sens3b-5abcd, results='asis'}
make.parameters.est.table(sens.models.3[[2]],
 caption = paste0("Posterior (2.5\\textsuperscript{th} percentile, Median, and ",
                   "97.5\\textsuperscript{th} percentile) and MPD ",
                   "estimates of key parameters ",
                  "for Sc 3b (mean ln(M)=ln(0.4), SD=0.1), Area 5ABCD. $R_0$ is in thousands of fish. $B_0$ is in tonnes. "),
  omit_pars = pars_est_omit)
```

```{r tab-param-table-sens3c-5abcd, results='asis'}
make.parameters.est.table(sens.models.3[[3]],
 caption = paste0("Posterior (2.5\\textsuperscript{th} percentile, Median, and ",
                   "97.5\\textsuperscript{th} percentile) and MPD ",
                   "estimates of key parameters ",
                  "for Sc 3c (mean ln(M)=ln(0.4), SD=0.2), Area 5ABCD. $R_0$ is in thousands of fish. $B_0$ is in tonnes. "),
  omit_pars = pars_est_omit)
```

```{r tab-param-table-sens4a-5abcd, results='asis'}
make.parameters.est.table(sens.models.4[[1]],
 caption = paste0("Posterior (2.5\\textsuperscript{th} percentile, Median, and ",
                   "97.5\\textsuperscript{th} percentile) and MPD ",
                   "estimates of key parameters ",
                  "for Sc 4a (Uniform prior for steepness), Area 5ABCD. $R_0$ is in thousands of fish. $B_0$ is in tonnes. "),
  omit_pars = pars_est_omit)
```

\clearpage

```{r tab-param-table-sens4b-5abcd, results='asis'}
make.parameters.est.table(sens.models.4[[2]],
 caption = paste0("Posterior (2.5\\textsuperscript{th} percentile, Median, and ",
                   "97.5\\textsuperscript{th} percentile) and MPD ",
                   "estimates of key parameters ",
                  "for Sc 4b (beta prior for steepness with mean = 0.85 and SD = 0.15), Area 5ABCD. $R_0$ is in thousands of fish. $B_0$ is in tonnes. "),
  omit_pars = pars_est_omit)
```

```{r tab-param-table-sens6a-5abcd, results='asis'}
make.parameters.est.table(sens.models.6[[1]],
 caption = paste0("Posterior (2.5\\textsuperscript{th} percentile, Median, and ",
                   "97.5\\textsuperscript{th} percentile) and MPD ",
                   "estimates of key parameters ",
                  "for Sc 6a ($\\sigma_{O}$ = 0.1), Area 5ABCD. $R_0$ is in thousands of fish. $B_0$ is in tonnes. "),
  omit_pars = pars_est_omit)
```

```{r tab-param-table-sens6b-5abcd, results='asis'}
make.parameters.est.table(sens.models.6[[2]],
 caption = paste0("Posterior (2.5\\textsuperscript{th} percentile, Median, and ",
                   "97.5\\textsuperscript{th} percentile) and MPD ",
                   "estimates of key parameters ",
                  "for Sc 6b ($\\sigma_{O}$ = 0.15), Area 5ABCD. $R_0$ is in thousands of fish. $B_0$ is in tonnes. "),
  omit_pars = pars_est_omit)
```

\clearpage

```{r tab-param-table-sens6c-5abcd, results='asis'}
make.parameters.est.table(sens.models.6[[3]],
 caption = paste0("Posterior (2.5\\textsuperscript{th} percentile, Median, and ",
                   "97.5\\textsuperscript{th} percentile) and MPD ",
                   "estimates of key parameters ",
                  "for Sc 6c ($\\sigma_{O}$ = 0.25), Area 5ABCD. $R_0$ is in thousands of fish. $B_0$ is in tonnes. "),
  omit_pars = pars_est_omit)
```


\clearpage

## SELECTED SENSITIVITY RESULTS: AREA 3CD

```{r tab-param-table-sens2a-3cd, results='asis'}
make.parameters.est.table(sens.models.9[[1]],
 caption = paste0("Posterior (2.5\\textsuperscript{th} percentile, Median, and ",
                   "97.5\\textsuperscript{th} percentile) and MPD ",
                   "estimates of key parameters ",
                  "for Sc 2a (sd of the WCVI Synoptic Survey was set to the same sd as for the QCS and HS Synoptic Surveys), Area 3CD. $R_0$ is in thousands of fish. $B_0$ is in tonnes. "),
  omit_pars = pars_est_omit)
```

```{r tab-param-table-sens2b-3cd, results='asis'}
make.parameters.est.table(sens.models.9[[2]],
 caption = paste0("Posterior (2.5\\textsuperscript{th} percentile, Median, and ",
                   "97.5\\textsuperscript{th} percentile) and MPD ",
                   "estimates of key parameters ",
                  "for Sc 2b (uniform priors for synoptic survey catchability), Area 3CD. $R_0$ is in thousands of fish. $B_0$ is in tonnes. "),
  omit_pars = pars_est_omit)
```

```{r tab-param-table-sens3a-3cd, results='asis'}
make.parameters.est.table(sens.models.10[[1]],
 caption = paste0("Posterior (2.5\\textsuperscript{th} percentile, Median, and ",
                   "97.5\\textsuperscript{th} percentile) and MPD ",
                   "estimates of key parameters ",
                  "for Sc 3a (mean ln(M)=ln(0.5), SD=0.2), Area 3CD. $R_0$ is in thousands of fish. $B_0$ is in tonnes. "),
  omit_pars = pars_est_omit)
```

\clearpage


```{r tab-param-table-sens3b-3cd, results='asis'}
make.parameters.est.table(sens.models.10[[2]],
 caption = paste0("Posterior (2.5\\textsuperscript{th} percentile, Median, and ",
                   "97.5\\textsuperscript{th} percentile) and MPD ",
                   "estimates of key parameters ",
                  "for Sc 3b (mean ln(M)=ln(0.4), SD=0.1), Area 3CD. $R_0$ is in thousands of fish. $B_0$ is in tonnes. "),
  omit_pars = pars_est_omit)
```

```{r tab-param-table-sens3c-3cd, results='asis'}
make.parameters.est.table(sens.models.10[[3]],
 caption = paste0("Posterior (2.5\\textsuperscript{th} percentile, Median, and ",
                   "97.5\\textsuperscript{th} percentile) and MPD ",
                   "estimates of key parameters ",
                  "for Sc 3c (mean ln(M)=ln(0.4), SD=0.2), Area 3CD. $R_0$ is in thousands of fish. $B_0$ is in tonnes. "),
  omit_pars = pars_est_omit)
```

```{r tab-param-table-sens4a-3cd, results='asis'}
make.parameters.est.table(sens.models.11[[1]],
 caption = paste0("Posterior (2.5\\textsuperscript{th} percentile, Median, and ",
                   "97.5\\textsuperscript{th} percentile) and MPD ",
                   "estimates of key parameters ",
                  "for Sc 4a (Uniform prior for steepness), Area 3CD. $R_0$ is in thousands of fish. $B_0$ is in tonnes. "),
  omit_pars = pars_est_omit)
```

\clearpage


```{r tab-param-table-sens4b-3cd, results='asis'}
make.parameters.est.table(sens.models.11[[2]],
 caption = paste0("Posterior (2.5\\textsuperscript{th} percentile, Median, and ",
                   "97.5\\textsuperscript{th} percentile) and MPD ",
                   "estimates of key parameters ",
                  "for Sc 4b (beta prior for steepness with mean = 0.85 and SD = 0.15), Area 3CD. $R_0$ is in thousands of fish. $B_0$ is in tonnes. "),
  omit_pars = pars_est_omit)
```

```{r tab-param-table-sens6a-3cd, results='asis'}
make.parameters.est.table(sens.models.13[[1]],
 caption = paste0("Posterior (2.5\\textsuperscript{th} percentile, Median, and ",
                   "97.5\\textsuperscript{th} percentile) and MPD ",
                   "estimates of key parameters ",
                  "for Sc 6a ($\\sigma_{O}$ = 0.1), Area 3CD. $R_0$ is in thousands of fish. $B_0$ is in tonnes. "),
  omit_pars = pars_est_omit)
```

```{r tab-param-table-sens6b-3cd, results='asis'}
make.parameters.est.table(sens.models.13[[2]],
 caption = paste0("Posterior (2.5\\textsuperscript{th} percentile, Median, and ",
                   "97.5\\textsuperscript{th} percentile) and MPD ",
                   "estimates of key parameters ",
                   "for Sc 6b ($\\sigma_{O}$ = 0.15), Area 3CD. $R_0$ is in thousands of fish. $B_0$ is in tonnes. "),
  omit_pars = pars_est_omit)
```

\clearpage


```{r tab-param-table-sens6c-3cd, results='asis'}
make.parameters.est.table(sens.models.13[[3]],
 caption = paste0("Posterior (2.5\\textsuperscript{th} percentile, Median, and ",
                   "97.5\\textsuperscript{th} percentile) and MPD ",
                   "estimates of key parameters ",
                  "for Sc 6c ($\\sigma_{O}$ = 0.25), Area 3CD. $R_0$ is in thousands of fish. $B_0$ is in tonnes. "),
  omit_pars = pars_est_omit)
```

\clearpage

## MODEL-AVERAGED REFERENCE POINTS AND DECISION TABLES {#sec:reference-points-and-decision-tables}


```{r tab-ref-points-table-avg-5abcd, results='asis'}
make.ref.points.table(c(base.model.5abcd,
                        sens.models.6.sub),
                      omit_msy = TRUE,
                      add.hist.ref = TRUE,
                      lrp = c(2000, 2000),
                      usr = c(1956, 2004),
                      digits = 2,
                      caption = paste0("Posterior (2.5\\textsuperscript{th} percentile, Median, and ",
                                       "97.5\\textsuperscript{th} percentile) of reference points for ",
                                       "model-averaged Area 5ABCD. ",
                                       "Biomass is in tonnes."))
```

\clearpage

```{r tab-post-biomass-avg-5abcd, results='asis'}
make.value.table(c(base.model.5abcd,
                        sens.models.6.sub),
                 1,
                 digits = 0,
                 caption = paste0("Posterior (2.5\\textsuperscript{th} percentile, Median, and 97.5\\textsuperscript{th} ",
                                  "percentile) and MPD estimates of biomass (t) for model-averaged Area 5ABCD."))
```

\clearpage

```{r tab-post-recr-avg-5abcd, results='asis'}
make.value.table(c(base.model.5abcd,
                        sens.models.6.sub),
                 2,
                 digits = 0,
                 caption = paste0("Posterior (2.5\\textsuperscript{th} percentile, Median, and 97.5\\textsuperscript{th} ",
                                  "percentile) and MPD estimates of recruitment (thousands) model-averaged Area 5ABCD."))
```

\clearpage

```{r tab-ref-points-table-avg-3cd, results='asis'}
make.ref.points.table(c(base.model.3cd,
                        sens.models.13.sub),
                      omit_msy = TRUE,
                      add.hist.ref = TRUE,
                      lrp = c(1986, 1986),
                      usr = c(1956, 2004),
                      digits = 2,
                      caption = paste0("Posterior (2.5\\textsuperscript{th} percentile, Median, and ",
                                       "97.5\\textsuperscript{th} percentile) of reference points for ",
                                       "model-averaged Area 3CD. ",
                                       "Biomass is in tonnes."))
```

\clearpage

```{r tab-post-biomass-avg-3cd, results='asis'}
make.value.table(c(base.model.3cd,
                        sens.models.13.sub),
                 1,
                 digits = 0,
                 caption = paste0("Posterior (2.5\\textsuperscript{th} percentile, Median, and 97.5\\textsuperscript{th} ",
                                  "percentile) and MPD estimates of biomass (t) for model-averaged Area 3CD."))
```

\clearpage

```{r tab-post-recr-avg-3cd, results='asis'}
make.value.table(c(base.model.3cd,
                        sens.models.13.sub),
                 2,
                 digits = 0,
                 caption = paste0("Posterior (2.5\\textsuperscript{th} percentile, Median, and 97.5\\textsuperscript{th} ",
                                  "percentile) and MPD estimates of recruitment (thousands) model-averaged Area 3CD."))
```

\clearpage

```{r tab-decision-avg-5abcd, results='asis'}
decision.table(avg.model.5abcd,
               caption = paste0("Decision table with model averaging for Area 5ABCD. Models averaged are: ",
                                and.string(c(base.model.5abcd.name, sens.models.name.6.sub)),
                                "."))
```

\clearpage

```{r tab-decision-avg-3cd, results='asis'}
decision.table(avg.model.3cd,
               caption = paste0("Decision table with model averaging for Area 3CD. Models averaged are: ",
                                and.string(c(base.model.3cd.name, sens.models.name.13.sub)),
                                "."))
```

\clearpage
