---
title: |
  2018 Pacific cod decision tables for Hecate Strait, Queen Charlotte Sound (5ABCD) and West Coast Vancouver Island (3CD)
author: |
  Robyn Forrest, Sean Anderson, Chris Grandin, Paul Starr
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      ratio: "16:9"
      titleSlideClass: [center, middle]
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
css: pcod.css

---

```{r setup, echo = FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      error = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      results = FALSE,
                      cache = TRUE,
                      autodep = TRUE,
                      cache.comments = FALSE,
                      fig.align = "center",
                      fig.width = 8,
                      fig.height = 5,
                      dev = 'svg',
                      fig.asp = 0.618)
options(htmltools.dir.version = FALSE)
```

```{r read-data, include = FALSE, cache=FALSE}
source(file.path(here::here(), "R", "all.R"))
build(ovwrt.base = FALSE,
      ovwrt.sens = FALSE,
      ovwrt.retro = FALSE,
      burnin = 1000,
      thin = 1)
load.models.into.parent.env()
source(file.path(rootd.R, "custom-knitr-variables.R"))
```


## Historical Biomass-based Reference points

**Limit reference point:**<br />
Lowest estimated biomass agreed to be an undesirable state to avoid:
  - 5ABCD: $B_{2000}$
  - 3CD:   $B_{1986}$

**Upper Stock Reference:**<br />
Average estimated biomass from 1956-2004

---

## Area 5ABCD
```{r fig-base-biomass-refpts-5ABCD}

b.plot(base.model.5abcd, base.model.5abcd.name, add.bo.ref=F, add.hist.ref=T, lrp=c(2000,2000), usr =c(1956,2004))
```

---

## Area 3CD
```{r fig-base-biomass-refpts-3CD}

b.plot(base.model.3cd, base.model.3cd.name, add.bo.ref=F, add.hist.ref=T, lrp=c(1986,1986), usr =c(1956,2004))
```



---

## Area 5ABCD - Reference case decision table - 1
<SPAN STYLE="font-size: 12pt">
```{r tab-decision-5abcd-1, results='asis'}
decision.table(base.model.5abcd,
               base.model.5abcd.name,
               format = "html",
               tac.vec = seq(0, 1000, 100))
```
</SPAN>

---
## Area 5ABCD - Reference case decision table - 2
<SPAN STYLE="font-size: 12pt">
```{r tab-decision-5abcd-2, results='asis'}
decision.table(base.model.5abcd,
               base.model.5abcd.name,
               format = "html",
               tac.vec = c(seq(1100, 2000, 100), 3000))
```
</SPAN>

---
## Area 5ABCD - Model averaged decision table
 - Scenarios included (agreed upon at Oct 11 2018 RPR meeting, PBS):
  - 1a Reference model
  - 2d Prior mean synoptic survey ln(q) = ln(1.0) (pro-rated by area)
  - 2e Increase prior SD for synoptic surveys to 0.6
  - 3a M prior mean = 0.4, SD = 0.1
  - 5a Knife-edged age at recruitment = 3 y
  - 6b $\sigma_O$ = 0.15
  - 7b $\sigma_W$ = 0.15

---
## Area 5ABCD - Scenarios used in decision table
```{r fig-dt-biomass-5abcd}
b.plot(c(base.model.5abcd, sens.models.6.sub), c(base.model.5abcd.name, sens.models.name.6.sub))
#b.plot(c(sens.models.6.sub), c(sens.models.name.6.sub))
```

---
## Area 5ABCD - Model averaged decision table - 1
<SPAN STYLE="font-size: 12pt">
```{r tab-decision-5abcd-avg-1, results='asis'}
decision.table(desc.models.5abcd,
               desc.models.5abcd.name,
               format = "html",
               tac.vec = seq(0, 1000, 100))
```
</SPAN>

---
## Area 5ABCD - Model averaged decision table - 2
<SPAN STYLE="font-size: 12pt">
```{r tab-decision-5abcd-avg-2, results='asis'}
decision.table(desc.models.5abcd,
               desc.models.5abcd.name,
               format = "html",
               tac.vec = c(seq(1100, 2000, 100), 3000))
```
</SPAN>

---
## Area 3CD - Reference case decision table
<SPAN STYLE="font-size: 10pt">
```{r tab-decision-3cd, results='asis'}
decision.table(base.model.3cd,
               base.model.3cd.name,
               format = "html")
```
</SPAN>

---
## Area 3CD - Model averaged decision tables
 - Scenarios included (agreed upon at Oct 11 2018 RPR meeting, PBS):
  - 1a Reference model
  - 2d Prior mean synoptic survey ln(q) = ln(1.0)
  - 2e Increase prior SD for synoptic surveys to 0.6
  - 3a M prior mean = 0.4, SD = 0.1
  - 5a Knife-edged age at recruitment = 3 y
  - 6b $\sigma_O$ = 0.15
  - 7b $\sigma_W$ = 0.15

---
## Area 3CD - Scenarios used in decision table
```{r fig-dt-biomass-3cd}
b.plot(c(base.model.3cd, sens.models.13.sub), c(base.model.3cd.name, sens.models.name.13.sub))
```


---
## Area 3CD - Model averaged decision table. 2018 Ct = 164.47 t
<SPAN STYLE="font-size: 10pt">
```{r tab-decision-3cd-avg, results='asis'}
decision.table(desc.models.3cd,
               desc.models.3cd.name,
               format = "html")
```
</SPAN>
